### 2020-07-22 paper/paper.tex
work on paper

\documentclass{article}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage[numbers]{natbib}

\bibliographystyle{plainnat}

\title{Formatting instructions for NeurIPS 2018}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.

\author{%
  Derek Koleber \\
  \texttt{derekkoleber@gmail.com}  
}

\begin{document}

\maketitle

\begin{abstract}
    One of the saught after objectives within neural architecture search
    is the reduction of search time. Some recent approaches attempt to reduce
    search time by using surrogate performance metric that predict performance
    based on learning curves and/or architecture embeddings. 
    In this paper, a architecture-agnostic, surrogate-model-less approach is explored as an accelerator for
    evolutionary-strategy-based neural architeure search, experimentally achieving
    acceleration of 8x while also providing benefits to exploration of the search space.
\end{abstract}

\section{Introduction}

    In recent years, various approaches to neural architecture search (NAS) have been 
successful in discovering neural architectures in a variety of computer vision
tasks as well as in language modeling, and INSERT SOMETHING. While many discovered architectures
have achieved state-of-the-art performance on popular computer benchmarks,
the compute cost of NAS acts as a significant obstacle.

    Works within the field have taken many different approaches to reducing search time.
Of the most significance to this work is the approach of using a performance surrogate,
which allows the prediction of an architecture's performance prior to training completion.
The effectiveness of different executions of approach manifest themselves in efficiency improvements 
all the way from early stopping to \cite{arch_pred_1} architecture analysis without the necessity to train.
\cite{snas} \cite{darts} 
\cite{arch_pred_1}
\cite{econas}
\cite{amoebanet}
\cite{acc_pred_1}
\cite{pnas}
\cite{lemonade}
\cite{nasnet}
\cite{learning_curve_1}
\cite{synthetic_samples}
\cite{snas}
\cite{enas}
\cite{cars}
\cite{rl_nas}
\cite{evolved_transformer}
\cite{multitask_1}
\cite{mnas}
\cite{obj_detection_1}
\cite{hardware_darts}

\subsection{Style}

Papers to be submitted to NeurIPS 2018 must be prepared according to the
instructions presented here. Papers may only be up to eight pages long,
including figures. Additional pages \emph{containing only acknowledgments and/or
  cited references} are allowed. Papers that exceed eight pages of content
(ignoring references) will not be reviewed, or in any other way considered for
presentation at the conference.

The margins in 2018 are the same as since 2007, which allow for $\sim$$15\%$
more words in the paper compared to earlier years.

Authors are required to use the NeurIPS \LaTeX{} style files obtainable at the
NeurIPS website as indicated below. Please make sure you use the current files
and not previous versions. Tweaking the style files may be grounds for
rejection.

\subsection{Retrieval of style files}

The style files for NeurIPS and other conference information are available on
the World Wide Web at
\begin{center}
  \url{http://www.neurips.cc/}
\end{center}
The file \verb+neurips_2018.pdf+ contains these instructions and illustrates the
various formatting requirements your NeurIPS paper must satisfy.

The only supported style file for NeurIPS 2018 is \verb+neurips_2018.sty+,
rewritten for \LaTeXe{}.  \textbf{Previous style files for \LaTeX{} 2.09,
  Microsoft Word, and RTF are no longer supported!}

The \LaTeX{} style file contains three optional arguments: \verb+final+, which
creates a camera-ready copy, \verb+preprint+, which creates a preprint for
submission to, e.g., arXiv, and \verb+nonatbib+, which will not load the
\verb+natbib+ package for you in case of package clash.

\paragraph{New preprint option for 2018}
If you wish to post a preprint of your work online, e.g., on arXiv, using the
NeurIPS style, please use the \verb+preprint+ option. This will create a
nonanonymized version of your work with the text ``Preprint. Work in progress.''
in the footer. This version may be distributed as you see fit. Please \textbf{do
  not} use the \verb+final+ option, which should \textbf{only} be used for
papers accepted to NeurIPS.

At submission time, please omit the \verb+final+ and \verb+preprint+
options. This will anonymize your submission and add line numbers to aid
review. Please do \emph{not} refer to these line numbers in your paper as they
will be removed during generation of camera-ready copies.

The file \verb+neurips_2018.tex+ may be used as a ``shell'' for writing your
paper. All you have to do is replace the author, title, abstract, and text of
the paper with your own.

The formatting instructions contained in these style files are summarized in
Sections \ref{gen_inst}, \ref{headings}, and \ref{others} below.

\section{General formatting instructions}
\label{gen_inst}

The text must be confined within a rectangle 5.5~inches (33~picas) wide and
9~inches (54~picas) long. The left margin is 1.5~inch (9~picas).  Use 10~point
type with a vertical spacing (leading) of 11~points.  Times New Roman is the
preferred typeface throughout, and will be selected for you by default.
Paragraphs are separated by \nicefrac{1}{2}~line space (5.5 points), with no
indentation.

The paper title should be 17~point, initial caps/lower case, bold, centered
between two horizontal rules. The top rule should be 4~points thick and the
bottom rule should be 1~point thick. Allow \nicefrac{1}{4}~inch space above and
below the title to rules. All pages should start at 1~inch (6~picas) from the
top of the page.

For the final version, authors' names are set in boldface, and each name is
centered above the corresponding address. The lead author's name is to be listed
first (left-most), and the co-authors' names (if different address) are set to
follow. If there is only one co-author, list both author and co-author side by
side.

Please pay special attention to the instructions in Section \ref{others}
regarding figures, tables, acknowledgments, and references.

\section{Headings: first level}
\label{headings}

All headings should be lower case (except for first word and proper nouns),
flush left, and bold.

First-level headings should be in 12-point type.

\subsection{Headings: second level}

Second-level headings should be in 10-point type.

\subsubsection{Headings: third level}

Third-level headings should be in 10-point type.

\paragraph{Paragraphs}

There is also a \verb+\paragraph+ command available, which sets the heading in
bold, flush left, and inline with the text, with the heading followed by 1\,em
of space.

\section{Citations, figures, tables, references}
\label{others}

These instructions apply to everyone.

\subsection{Citations within the text}

The \verb+natbib+ package will be loaded for you by default.  Citations may be
author/year or numeric, as long as you maintain internal consistency.  As to the
format of the references themselves, any style is acceptable as long as it is
used consistently.

The documentation for \verb+natbib+ may be found at
\begin{center}
  \url{http://mirrors.ctan.org/macros/latex/contrib/natbib/natnotes.pdf}
\end{center}
Of note is the command \verb+\citet+, which produces citations appropriate for
use in inline text.  For example,
\begin{verbatim}
   \citet{hasselmo} investigated\dots
\end{verbatim}
produces
\begin{quote}
  Hasselmo, et al.\ (1995) investigated\dots
\end{quote}

If you wish to load the \verb+natbib+ package with options, you may add the
following before loading the \verb+neurips_2018+ package:
\begin{verbatim}
   \PassOptionsToPackage{options}{natbib}
\end{verbatim}

If \verb+natbib+ clashes with another package you load, you can add the optional
argument \verb+nonatbib+ when loading the style file:
\begin{verbatim}
   \usepackage[nonatbib]{neurips_2018}
\end{verbatim}

As submission is double blind, refer to your own published work in the third
person. That is, use ``In the previous work of Jones et al.\ [4],'' not ``In our
previous work [4].'' If you cite your other papers that are not widely available
(e.g., a journal paper under review), use anonymous author names in the
citation, e.g., an author of the form ``A.\ Anonymous.''

\subsection{Footnotes}

Footnotes should be used sparingly.  If you do require a footnote, indicate
footnotes with a number\footnote{Sample of the first footnote.} in the
text. Place the footnotes at the bottom of the page on which they appear.
Precede the footnote with a horizontal rule of 2~inches (12~picas).

Note that footnotes are properly typeset \emph{after} punctuation
marks.\footnote{As in this example.}

\subsection{Figures}

\begin{figure}
  \centering
  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
  \caption{Sample figure caption.}
\end{figure}

All artwork must be neat, clean, and legible. Lines should be dark enough for
purposes of reproduction. The figure number and caption always appear after the
figure. Place one line space before the figure caption and one line space after
the figure. The figure caption should be lower case (except for first word and
proper nouns); figures are numbered consecutively.

You may use color figures.  However, it is best for the figure captions and the
paper body to be legible if the paper is printed in either black/white or in
color.

\subsection{Tables}

All tables must be centered, neat, clean and legible.  The table number and
title always appear before the table.  See Table~\ref{sample-table}.

Place one line space before the table title, one line space after the
table title, and one line space after the table. The table title must
be lower case (except for first word and proper nouns); tables are
numbered consecutively.

Note that publication-quality tables \emph{do not contain vertical rules.} We
strongly suggest the use of the \verb+booktabs+ package, which allows for
typesetting high-quality, professional tables:
\begin{center}
  \url{https://www.ctan.org/pkg/booktabs}
\end{center}
This package was used to typeset Table~\ref{sample-table}.

\begin{table}
  \caption{Sample table title}
  \label{sample-table}
  \centering
  \begin{tabular}{lll}
    \toprule
    \multicolumn{2}{c}{Part}                   \\
    \cmidrule(r){1-2}
    Name     & Description     & Size ($\mu$m) \\
    \midrule
    Dendrite & Input terminal  & $\sim$100     \\
    Axon     & Output terminal & $\sim$10      \\
    Soma     & Cell body       & up to $10^6$  \\
    \bottomrule
  \end{tabular}
\end{table}

\section{Final instructions}

Do not change any aspects of the formatting parameters in the style files.  In
particular, do not modify the width or length of the rectangle the text should
fit into, and do not change font sizes (except perhaps in the
\textbf{References} section; see below). Please note that pages should be
numbered.

\section{Preparing PDF files}

Please prepare submission files with paper size ``US Letter,'' and not, for
example, ``A4.''

Fonts were the main cause of problems in the past years. Your PDF file must only
contain Type 1 or Embedded TrueType fonts. Here are a few instructions to
achieve this.

\begin{itemize}

\item You should directly generate PDF files using \verb+pdflatex+.

\item You can check which fonts a PDF files uses.  In Acrobat Reader, select the
  menu Files$>$Document Properties$>$Fonts and select Show All Fonts. You can
  also use the program \verb+pdffonts+ which comes with \verb+xpdf+ and is
  available out-of-the-box on most Linux machines.

\item The IEEE has recommendations for generating PDF files whose fonts are also
  acceptable for NeurIPS. Please see
  \url{http://www.emfield.org/icuwb2010/downloads/IEEE-PDF-SpecV32.pdf}

\item \verb+xfig+ "patterned" shapes are implemented with bitmap fonts.  Use
  "solid" shapes instead.

\item The \verb+\bbold+ package almost always uses bitmap fonts.  You should use
  the equivalent AMS Fonts:
\begin{verbatim}
   \usepackage{amsfonts}
\end{verbatim}
followed by, e.g., \verb+\mathbb{R}+, \verb+\mathbb{N}+, or \verb+\mathbb{C}+
for $\mathbb{R}$, $\mathbb{N}$ or $\mathbb{C}$.  You can also use the following
workaround for reals, natural and complex:
\begin{verbatim}
   \newcommand{\RR}{I\!\!R} %real numbers
   \newcommand{\Nat}{I\!\!N} %natural numbers
   \newcommand{\CC}{I\!\!\!\!C} %complex numbers
\end{verbatim}
Note that \verb+amsfonts+ is automatically loaded by the \verb+amssymb+ package.

\end{itemize}

If your file contains type 3 fonts or non embedded TrueType fonts, we will ask
you to fix it.

\subsection{Margins in \LaTeX{}}

Most of the margin problems come from figures positioned by hand using
\verb+\special+ or other commands. We suggest using the command
\verb+\includegraphics+ from the \verb+graphicx+ package. Always specify the
figure width as a multiple of the line width as in the example below:
\begin{verbatim}
   \usepackage[pdftex]{graphicx} ...
   \includegraphics[width=0.8\linewidth]{myfile.pdf}
\end{verbatim}
See Section 4.4 in the graphics bundle documentation
(\url{http://mirrors.ctan.org/macros/latex/required/graphics/grfguide.pdf})

A number of width problems arise when \LaTeX{} cannot properly hyphenate a
line. Please give LaTeX hyphenation hints using the \verb+\-+ command when
necessary.

\subsubsection*{Acknowledgments}

Use unnumbered third level headings for the acknowledgments. All acknowledgments
go at the end of the paper. Do not include acknowledgments in the anonymized
submission, only in the final paper.

\section*{References}

References follow the acknowledgments. Use unnumbered first-level heading for
the references. Any choice of citation style is acceptable as long as you are
consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
when listing the references. {\bf Remember that you can use more than eight
  pages as long as the additional pages contain \emph{only} cited references.}
\medskip

\small

\bibliography{reference}

\end{document}

### 2020-07-22 src/relative_predictions/RelativePredictions.py

@@ -571,15 +571,15 @@ def multi_config_test():
     # multi_model_test('zs_small', num_models=num_models, hparams=small_params(32), emb_queue=embeddings)
     # multi_model_test('zs_medium', num_models=num_models, hparams=medium_params(32), emb_queue=embeddings)
     # multi_model_test('zs_tiny', num_models=num_models, hparams=tiny_params(32), emb_queue=embeddings)
-    multi_model_test('zs_standard_6x3_32e_32f', num_models=num_models, hparams=medium_params(32), emb_queue=embeddings)
+    # multi_model_test('zs_standard_6x3_32e_32f', num_models=num_models, hparams=medium_params(32), emb_queue=embeddings)
     multi_model_test('zs_medium_6x3_16e_32f', num_models=num_models, hparams=medium_params(16), emb_queue=embeddings)
     multi_model_test('zs_small_3x3_16e_24f', num_models=num_models, hparams=small_params(16), emb_queue=embeddings)
     multi_model_test('zs_long_16', num_models=num_models, hparams=long_params(), emb_queue=long_embeddings)
 
 
 if __name__ == '__main__':
-    analyze_multiple()
-    # multi_config_test()
+    # analyze_multiple()
+    multi_config_test()
 
     # analyze_stuff('zs_set_1\\zs_medium')
     # analyze_stuff('zs_small')

### 2020-07-22 src/relative_predictions/RelativePredictions.py
more data

@@ -138,6 +138,7 @@ def spearman_coef_distinct(rankings_predicted, rankings_actual):
 
     return 1. - (top/bottom)
 
+
 def spearman_coef(rankings_predicted, rankings_actual):
     n = len(rankings_predicted)
     if n < 2:
@@ -151,6 +152,7 @@ def spearman_coef(rankings_predicted, rankings_actual):
         return 1.
 
     return cov / (std_pred*std_act)
+
 
 def analyze_slices(dir_name):
     dir_path = os.path.join(evo_dir, dir_name)
@@ -414,7 +416,7 @@ def analyze_multiple():
         return accuracies
 
 
-    dir_names = ['zs_standard_6x3_32e_32f', 'zs_small_3x3_32e_24f', 'zs_medium_5x3_16e_32f', 'zs_medium_5x3_16e_24f']
+    dir_names = ['zs_standard_6x3_32e_32f', 'zs_small_3x3_32e_24f', 'zs_medium_5x3_16e_32f', 'zs_medium_5x3_16e_24f', 'zs_medium_6x3_16e_32f']
 
     accuracies = [load_accuracies(x) for x in dir_names]
 
@@ -443,9 +445,13 @@ def analyze_multiple():
         for index_set in indexes:
             np.random.shuffle(index_set)
 
+
+        rank_corrs = []
         for simulation in indexes:
             # print(f'simulating: {simulation}')
-            results.append([[],[],[],[]])
+            results.append([[],[],[],[],[]])
+            ranks = []
+            rank_distances = []
             for num_models_so_far, master_model_index in enumerate(simulation):
 
                 model_accuracies_up_to_point_final = [accs[i][-1] for i in simulation[:num_models_so_far + 1]]
@@ -467,25 +473,48 @@ def analyze_multiple():
 
                 average_rank_distance = np.mean([abs(np.where(ranks_prediction==i)[0] - np.where(ranks_actual==i)[0]) for i in range(num_models_so_far+1)]) if num_models_so_far >= 1 else 0
 
-                this_rank_distance = abs(np.where(ranks_prediction==num_models_so_far)[0] - np.where(ranks_actual==num_models_so_far)[0]) if num_models_so_far >= 1 else 0
+                this_rank_prediction = np.where(ranks_prediction==num_models_so_far)[0][0]
+                this_rank_actual = np.where(ranks_actual==num_models_so_far)[0][0]
[…]

### 2020-07-22 src/relative_predictions/nas_bench_201_analysis.py

@@ -1,0 +1,30 @@
+from nas_201_api import NASBench201API as nasapi
+import os
+import sys
+
+HERE = os.path.dirname(os.path.abspath(__file__))
+sys.path.append(os.path.join(HERE,'..\\'))
+
+from FileManagement import *
+
+def test():
+    file_name = 'NAS-Bench-201-v1_1-096897.pth'
+    file_path = os.path.join(res_dir, file_name)
+
+    if os.path.exists(file_path):
+        api = nasapi(file_path)
+
+        num = len(api)
+        print(f'api size: {num}')
+        info = api.query_meta_info_by_index(1)
+        print(f'info {info}')
+        metrics = info.get_metrics('cifar10', 'test')
+        print(f'metrics: {metrics}')
+        test_acc = metrics['top1']
+        print(f'test_acc: {test_acc}')
+        # for i, arch_str in enumerate(api):
+        #     print('{:5d}/{:5d} : {:}'.format(i, len(api), arch_str))
+
+
+if __name__ == '__main__':
+    test()

### 2020-08-22 paper/paper.tex
WIP

@@
-\documentclass{article}
+\documentclass[twocolumn]{article}
+\usepackage[bottom=10em,top=10em,right=5em,left=5em]{geometry}
 
@@
 \usepackage[numbers]{natbib}
+\usepackage{pgfplots}
+\usepackage{layouts}
+\usepackage{placeins}
+\usepackage{layout}
 
 \bibliographystyle{plainnat}
+\setlength{\headsep}{5pt}
 
-\title{Formatting instructions for NeurIPS 2018}
-
-% The \author macro works with any number of authors. There are two commands
-% used to separate the names and addresses of multiple authors: \And and \AND.
-%
-% Using \And between authors leaves it to LaTeX to determine where to break the
-% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
-% authors names on the first line, and the last on the second line, try using
-% \AND instead of \And before the third author name.
+\title{Placeholder Title}
 
@@
     based on learning curves and/or architecture embeddings. 
-    In this paper, a architecture-agnostic, surrogate-model-less approach is explored as an accelerator for
-    evolutionary-strategy-based neural architeure search, experimentally achieving
-    acceleration of 8x while also providing benefits to exploration of the search space.
+    In this paper, the efficacy of purely statistical methodology for accelerating
+    the search time of evolutionary algorithm oriented NAS approaches is assessed. Analysis of results
+    suggests that statistical methods do not provide meaningful search time reductions
+    within commonly used NAS search spaces.
 \end{abstract}
@@
 
-\subsection{Style}
+\subsection{Background and Related Work}
 
-Papers to be submitted to NeurIPS 2018 must be prepared according to the
-instructions presented here. Papers may only be up to eight pages long,
-including figures. Additional pages \emph{containing only acknowledgments and/or
-  cited references} are allowed. Papers that exceed eight pages of content
-(ignoring references) will not be reviewed, or in any other way considered for
-presentation at the conference.
+For NAS approaches utilizing genetic evolutionary algorithms, the means with which the algorithm determines the most and least fit candidates 
+for mutation and optionally removal hinges upon the ability to determine comparative performance between candidates. The go-to metric for 
+determining the performance of candidates with single-objective models is validation or test accuracy or error. However, recent approaches 
+have forgone ratio variables to measure perforance in favor of ordinal variables \cite{pnas}, since relative performance is the only necessity 
+for common selection strategies like traditional tournament selection and its variations, such as aging selection \cite{amoebanet}. 
+In the case of PNAS \cite{pnas}, a surrogate model is used to predict model performance in a way that ranks models approximately as they would
+be ranked as they would be using actual performance.
 
-The margins in 2018 are the same as since 2007, which allow for $\sim$$15\%$
-more words in the paper compared to earlier years.
+\subsection{Approach}
 
-Authors are required to use the NeurIPS \LaTeX{} style files obtainable at the
-NeurIPS website as indicated below. Please make sure you use the current files
-and not previous versions. Tweaking the style files may be grounds for
-rejection.
+Using a surrogate model to predict model rank has the downside of training surrogate model to predict in a space that's growing in parallel with the
+surrogate. PNAS \cite{pnas} proposes a clever solution to this which allows the surrogate to train over more data during the beginning of search.
+Its proposed approach is only possible due to the fact that the PNAS search space has the capability to expand its search space in a way that
+allows the initial, smaller search spaces to be representative of the later, larger search spaces in a way that is meaningful to the surrogate.
+Such an approach doesn't provide benefits to search spaces that aren't expandable in a manner similar to that of PNAS, which means a surrogate would
+have to train on architectures representing a complete search space.
 
-\subsection{Retrieval of style files}
+Surrogate models are not the only way to predict candidate ranking. Two ways to represent relative performances of a population of candidates are the following 'performance metrics':
 
-The style files for NeurIPS and other conference information are available on
-the World Wide Web at
-\begin{center}
-  \url{http://www.neurips.cc/}
-\end{center}
-The file \verb+neurips_2018.pdf+ contains these instructions and illustrates the
-various formatting requirements your NeurIPS paper must satisfy.
+- Raw Rank Measurements Based on Candidate Accuracy
 
-The only supported style file for NeurIPS 2018 is \verb+neurips_2018.sty+,
-rewritten for \LaTeXe{}.  \textbf{Previous style files for \LaTeX{} 2.09,
-  Microsoft Word, and RTF are no longer supported!}
+Rank measurements are a clear way to represent accuracies as ordinal data. No additional explanation is necessary.
 
-The \LaTeX{} style file contains three optional arguments: \verb+final+, which
-creates a camera-ready copy, \verb+preprint+, which creates a preprint for
-submission to, e.g., arXiv, and \verb+nonatbib+, which will not load the
-\verb+natbib+ package for you in case of package clash.
+- Z-Scores of Candidate Accuracy
 
-\paragraph{New preprint option for 2018}
-If you wish to post a preprint of your work online, e.g., on arXiv, using the
-NeurIPS style, please use the \verb+preprint+ option. This will create a
-nonanonymized version of your work with the text ``Preprint. Work in progress.''
-in the footer. This version may be distributed as you see fit. Please \textbf{do
-  not} use the \verb+final+ option, which should \textbf{only} be used for
-papers accepted to NeurIPS.
+Zz-scores of candidate performance can somewhat act as interval data and thus can better represent outliers and clusters in comparison to raw ranks. 
+Z-Scores are typically used with normal distributions.
+Model accuracies in NASBench 201 \cite{nasbench201} provide a complete view of the distributions of accuracies in what could be considered to be 
+a search space representative of common NAS search spaces. 
+An Anderson-Darling test over model test accuracies for Cifar10 (200 epochs) in NASBench201 produces a test statistic of 2717.199 
+(718.514 after a Box-Cox transform) indicates at all significance levels that model accuracies do not fall into a normal distribution. 
+Nonetheless, z-scores still provide a way to judge relative model performance.
 
-At submission time, please omit the \verb+final+ and \verb+preprint+
-options. This will anonymize your submission and add line numbers to aid
-review. Please do \emph{not} refer to these line numbers in your paper as they
-will be removed during generation of camera-ready copies.
+The relevant benefit of ordinal and interval performance metrics is that a population's measurements evaluated at an early epoch are 
+directly comparable to its measurements at a later epoch. This is the basis for the possibility of search time acceleration, since
+the early performances have the potential to be predictive of final performances.
 
-The file \verb+neurips_2018.tex+ may be used as a ``shell'' for writing your
-paper. All you have to do is replace the author, title, abstract, and text of
-the paper with your own.
+% \printinunitsof{in}\prntlen{\textwidth}
 
-The formatting instructions contained in these style files are summarized in
-Sections \ref{gen_inst}, \ref{headings}, and \ref{others} below.
+\subsection{Stochastic Search Experimentation}
 
-\section{General formatting instructions}
-\label{gen_inst}
+\subsubsection{Experiment Details}
+To measure the potential of the use of z-scores and raw ranks as a predictors of final performance, populations of models are used to
+emulate a stochastic search that is accelerated by early performance prediction. 
+While stochastic search is a far-from-optimal search algorithm, this experiment's goal is rather to provide insight into the reliability 
+using the two performance predictors to find the best candidates at different population sizes.
 
-The text must be confined within a rectangle 5.5~inches (33~picas) wide and
-9~inches (54~picas) long. The left margin is 1.5~inch (9~picas).  Use 10~point
-type with a vertical spacing (leading) of 11~points.  Times New Roman is the
-preferred typeface throughout, and will be selected for you by default.
-Paragraphs are separated by \nicefrac{1}{2}~line space (5.5 points), with no
-indentation.
+Two populations of trained models from two different architecutre search spaces are sampled for this purpose.
+The first population is generated using a variety of hyperparemeter combinations within a search space similar to that of NASNet \cite{nasnet}.
+Implementation details of this search space are provided in the appendix. 
+The second population is a sampled subset of the architectures in NASBench201 \cite{nasbench201}.
 
-The paper title should be 17~point, initial caps/lower case, bold, centered
-between two horizontal rules. The top rule should be 4~points thick and the
-bottom rule should be 1~point thick. Allow \nicefrac{1}{4}~inch space above and
-below the title to rules. All pages should start at 1~inch (6~picas) from the
-top of the page.
+Each population $P$ is evaluated at each combination between elements of $E^s$, $W^s$, and $M$.
+Each such evaluation at a given combination is referred to as a \emph{simulation}.
+The set of \emph{prediction epoch scalars} $E^s$ scales $t$, the total number of epochs per model in $P$,
+to produce the actual \emph{prediction epochs} at which final model performance rank will be predicted, $E^{a}$.
+This facilitates early performance prediction and thus the potential for search acceleration.
+The set of \emph{prediction window scalars} $W^s$ scales $E^a$ to produce the actual \emph{prediction windows} to be used 
+over trained epochs to be used during evaluation, $W^a$.
+The set of \emph{evaluation metric} functions $M$ includes functions for calculating an evaluation metric,
+given a model, a prediction epoch, and a prediction window. 
+These metric functions include averaged-over-window z-score measurements \emph{zm}'s, and raw rank measurements \emph{rm}'s.
 
-For the final version, authors' names are set in boldface, and each name is
-centered above the corresponding address. The lead author's name is to be listed
-first (left-most), and the co-authors' names (if different address) are set to
-follow. If there is only one co-author, list both author and co-author side by
-side.
+\[E^s = \{1, 0.5, 0.25, 0.125\}\]
+\[W^s = \{1, 0.5, 0.25, 0.001\}\]
+\[M = \{f_{zm}, f_{rm}\}\]
 
-Please pay special attention to the instructions in Section \ref{others}
-regarding figures, tables, acknowledgments, and references.
+\[f_{zm}(x, e, w) = \frac{1}{e-w}\sum_{i=e-w}^{e}\frac{x_i - \mu_i}{\sigma_i}\]
+\[f_{rm}(x, e, w) = \frac{1}{e-w}\sum_{i=e-w}^{e}r_{x_{i}}(P)\]
+
+\[predictions(P, e, w, f_{predictor}) = r(map(P, f_{predictor}))\]
+
+\[r(P) = rank\ of\ every\ element\ in\ P\]
+\[r_{x}(P) = rank\ of\ x\ within\ P\]
+
+In each simulation, $P$ is shuffled then evaluated as an incremental subset of the shuffled population.
+Thus, each simulation evaluates a simulated population as if it were growing to its final size, while using
+the evaluation metrics to estimate simulated population rankings at each step.
+This allows a direct comparison between the predicted rankings and actual rankings at each increment.
+Simlar to PNAS \cite{pnas}, the Spearman Coefficient is chosen to judge the reliability of early prediction of population performance ranks.
+At the addition of each subsequent model to the simulated population, average rank error, rank error for the newest model (new rank error), and the Spearman Coefficient
+for the population are measured and used as evaluation metrics. 
+Each simulation is run $N$ times, and evaluation metrics are averaged across simulation iterations. 
+Refer to the Figure ~\ref{fig:nasnet_1x_acceleration}, ~\ref{fig:nasnet_2x_acceleration}, ~\ref{fig:nasnet_4x_acceleration}, and ~\ref{fig:nasnet_8x_acceleration} in Appendix for simulation results.
+Additionally, the correlation between new models' predicted rank error and new models' predicted rank is measured for each simulation,
+and results are averaged across simulation iterations. These results can be found in Figure ~\ref{fig:rank_error_correlations}.
+
+\subsubsection{Analysis}
+
+\textbf{Higher acceleration rates result in higher average and new rank error, and lower Spearman coefficients.}
+New rank error and Spearman ccoefficients converge to levels that show clear trend that increases with acceleration rate.
+This is unsurprising, as these measurements are based on model performance that are further away in terms of epochs to their
+otherwise final performance. 
+As acceleration rate increases, average rank error comes closer to stabilizing around $\frac{1}{3}$, the expected average error rate
+for a random population, but the rank predictions causing such a rank error are clearly not random since the Spearman coefficient is far from zero.
+
+\textbf{New rank error stabilizes at a lower value than average rank error.}
+In all simulations, new rank error appears to stabilize at approximately half the value of the average rank error.
+Additionally, new rank error stabilizes faster than average rank error, stabilizing near a population of 4 while
+average rank error begins to stabilize around a population of 12.
+
+\textbf{Model size appears to impact performance prediction accuracy.} 
+The NASNet model population is comprised of models which all are larger than their NASBench201 counterparts.
+With NASNet simulations, Spearman coefficients remain consistenly higher and new rank error levels off at a lower value in comparison to NASBench201 simulations.
+Nonetheless, NASNet simulations show an average rank error trajectories similar to the trajectories that NASBench201 simulations play out.
+\textbf{Where do average rank error/new rank error/spearman coeff actually level out to? - take last quarter and average it?}
+
+\textbf{Prediction based on zscores and prediction based on raw ranks produce virtually the same results.}
+This is more evident with NASBench201 since it draws out to a higher population size. 
+\textbf{CORRELATION?}
+
+\textbf{New rank error has an overall weak-to-moderate positive correlation with the predicted new rank itself.}
+This trend is better observed with NASBench201 simulations, due to the fact that its larger simulated population will produce an innately more accurate
+representation of such a trend. 
+\textbf{HOW DOES THIS CORRELATE WITH INCREASING ACCELERATION RATE?}
+This trend can be interpreted optimistically to suggest that, in an evolution context, degrees of exploration will be bolstered
+outside of the exploration facilitated by the evolutionary algorithm alone. 
+Pessimistically, this trend can be interpreted to suggest that suboptimal candidates might be chosen during the selection step of
+evolutionary selection algorithms, resulting in slower time to find better candidates or the possibility for better candidates
+to be spuriously removed.
+
+\section{Aging Search Experimentation}
+
+Results from stochastic search experimentation are only applicable to an evolutionary algorithm context during the population's development prior to 
+selection mechanisms taking effect, since selection mechanisms generally increase the frequency of higher-performance candidates. 
+With a higher concentration of highly-performaning candidates in a population, the given evaluation metrics might perform less reliably.
+
+testtest
 
@@
 Third-level headings should be in 10-point type.
-
-\paragraph{Paragraphs}
-
-There is also a \verb+\paragraph+ command available, which sets the heading in
-bold, flush left, and inline with the text, with the heading followed by 1\,em
-of space.
-
-\section{Citations, figures, tables, references}
-\label{others}
-
-These instructions apply to everyone.
-
-\subsection{Citations within the text}
-
-The \verb+natbib+ package will be loaded for you by default.  Citations may be
-author/year or numeric, as long as you maintain internal consistency.  As to the
-format of the references themselves, any style is acceptable as long as it is
-used consistently.
-
-The documentation for \verb+natbib+ may be found at
-\begin{center}
-  \url{http://mirrors.ctan.org/macros/latex/contrib/natbib/natnotes.pdf}
-\end{center}
-Of note is the command \verb+\citet+, which produces citations appropriate for
-use in inline text.  For example,
-\begin{verbatim}
-   \citet{hasselmo} investigated\dots
-\end{verbatim}
-produces
-\begin{quote}
-  Hasselmo, et al.\ (1995) investigated\dots
-\end{quote}
-
-If you wish to load the \verb+natbib+ package with options, you may add the
-following before loading the \verb+neurips_2018+ package:
-\begin{verbatim}
-   \PassOptionsToPackage{options}{natbib}
-\end{verbatim}
-
-If \verb+natbib+ clashes with another package you load, you can add the optional
-argument \verb+nonatbib+ when loading the style file:
-\begin{verbatim}
-   \usepackage[nonatbib]{neurips_2018}
-\end{verbatim}
-
-As submission is double blind, refer to your own published work in the third
-person. That is, use ``In the previous work of Jones et al.\ [4],'' not ``In our
-previous work [4].'' If you cite your other papers that are not widely available
-(e.g., a journal paper under review), use anonymous author names in the
-citation, e.g., an author of the form ``A.\ Anonymous.''
 
@@
 
-All tables must be centered, neat, clean and legible.  The table number and
-title always appear before the table.  See Table~\ref{sample-table}.
-
-Place one line space before the table title, one line space after the
-table title, and one line space after the table. The table title must
-be lower case (except for first word and proper nouns); tables are
-numbered consecutively.
-
-Note that publication-quality tables \emph{do not contain vertical rules.} We
-strongly suggest the use of the \verb+booktabs+ package, which allows for
-typesetting high-quality, professional tables:
-\begin{center}
-  \url{https://www.ctan.org/pkg/booktabs}
-\end{center}
-This package was used to typeset Table~\ref{sample-table}.
-
 \begin{table}
@@
 
-\section{Final instructions}
-
-Do not change any aspects of the formatting parameters in the style files.  In
-particular, do not modify the width or length of the rectangle the text should
-fit into, and do not change font sizes (except perhaps in the
-\textbf{References} section; see below). Please note that pages should be
-numbered.
-
-\section{Preparing PDF files}
-
-Please prepare submission files with paper size ``US Letter,'' and not, for
-example, ``A4.''
-
-Fonts were the main cause of problems in the past years. Your PDF file must only
-contain Type 1 or Embedded TrueType fonts. Here are a few instructions to
-achieve this.
-
-\begin{itemize}
-
-\item You should directly generate PDF files using \verb+pdflatex+.
-
-\item You can check which fonts a PDF files uses.  In Acrobat Reader, select the
-  menu Files$>$Document Properties$>$Fonts and select Show All Fonts. You can
-  also use the program \verb+pdffonts+ which comes with \verb+xpdf+ and is
-  available out-of-the-box on most Linux machines.
-
-\item The IEEE has recommendations for generating PDF files whose fonts are also
-  acceptable for NeurIPS. Please see
-  \url{http://www.emfield.org/icuwb2010/downloads/IEEE-PDF-SpecV32.pdf}
-
-\item \verb+xfig+ "patterned" shapes are implemented with bitmap fonts.  Use
-  "solid" shapes instead.
-
-\item The \verb+\bbold+ package almost always uses bitmap fonts.  You should use
-  the equivalent AMS Fonts:
-\begin{verbatim}
-   \usepackage{amsfonts}
-\end{verbatim}
-followed by, e.g., \verb+\mathbb{R}+, \verb+\mathbb{N}+, or \verb+\mathbb{C}+
-for $\mathbb{R}$, $\mathbb{N}$ or $\mathbb{C}$.  You can also use the following
-workaround for reals, natural and complex:
-\begin{verbatim}
-   \newcommand{\RR}{I\!\!R} %real numbers
-   \newcommand{\Nat}{I\!\!N} %natural numbers
-   \newcommand{\CC}{I\!\!\!\!C} %complex numbers
-\end{verbatim}
-Note that \verb+amsfonts+ is automatically loaded by the \verb+amssymb+ package.
-
-\end{itemize}
-
-If your file contains type 3 fonts or non embedded TrueType fonts, we will ask
-you to fix it.
-
-\subsection{Margins in \LaTeX{}}
-
-Most of the margin problems come from figures positioned by hand using
-\verb+\special+ or other commands. We suggest using the command
-\verb+\includegraphics+ from the \verb+graphicx+ package. Always specify the
-figure width as a multiple of the line width as in the example below:
-\begin{verbatim}
-   \usepackage[pdftex]{graphicx} ...
-   \includegraphics[width=0.8\linewidth]{myfile.pdf}
-\end{verbatim}
-See Section 4.4 in the graphics bundle documentation
-(\url{http://mirrors.ctan.org/macros/latex/required/graphics/grfguide.pdf})
-
-A number of width problems arise when \LaTeX{} cannot properly hyphenate a
-line. Please give LaTeX hyphenation hints using the \verb+\-+ command when
-necessary.
-
-\subsubsection*{Acknowledgments}
-
-Use unnumbered third level headings for the acknowledgments. All acknowledgments
-go at the end of the paper. Do not include acknowledgments in the anonymized
-submission, only in the final paper.
-
-\section*{References}
-
-References follow the acknowledgments. Use unnumbered first-level heading for
-the references. Any choice of citation style is acceptable as long as you are
-consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
-when listing the references. {\bf Remember that you can use more than eight
-  pages as long as the additional pages contain \emph{only} cited references.}
-\medskip
-
-\small
-
 \bibliography{reference}
 
+\FloatBarrier
+\clearpage
+\onecolumn
+\appendix
+\section{Appendix}
+\subsection{Stochastic Search Results}
+\subsubsection{NASNet Simulations}
+\begin{figure}[!h]
+    \begin{center}
+        \input{../evolution/nasnet_1.0x_acceleration.pgf}
+    \end{center}
+    \caption{NASNet Simulation with 1x Acceleration}
+    \label{fig:nasnet_1x_acceleration}
+\end{figure}
+\begin{figure}
+    \begin{center}
+        \input{../evolution/nasnet_2.0x_acceleration.pgf}
+    \end{center}
+    \caption{NASNet Simulation with 2x Acceleration}
+    \label{fig:nasnet_2x_acceleration}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+        \input{../evolution/nasnet_4.0x_acceleration.pgf}
+    \end{center}
+    \caption{NASNet Simulation with 4x Acceleration}
+    \label{fig:nasnet_4x_acceleration}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+        \input{../evolution/nasnet_8.0x_acceleration.pgf}
+    \end{center}
+    \caption{NASNet Simulation with 8x Acceleration}
+    \label{fig:nasnet_8x_acceleration}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+        \input{../evolution/nasnet_rank_error_correlations.pgf}
+    \end{center}
+    \caption{NASNet Rank Error Correlations with Rank}
+    \label{fig:nasnet_rank_error_correlations}
+\end{figure}
+
+\FloatBarrier
+\clearpage
+\subsubsection{NASBench201 Simulations}
+
+\begin{figure}[!h]
+    \begin{center}
+        \input{../evolution/nasbench_16_1.0x_acceleration.pgf}
+    \end{center}
+    \caption{NASBench201 Simulation with 1x Acceleration}
+    \label{fig:nasbench_1x_acceleration}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+        \input{../evolution/nasbench_16_2.0x_acceleration.pgf}
+    \end{center}
+    \caption{NASBench201 Simulation with 2x Acceleration}
+    \label{fig:nasbench_2x_acceleration}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+        \input{../evolution/nasbench_16_4.0x_acceleration.pgf}
+    \end{center}
+    \caption{NASBench201 Simulation with 4x Acceleration}
+    \label{fig:nasbench_4x_acceleration}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+        \input{../evolution/nasbench_16_8.0x_acceleration.pgf}
+    \end{center}
+    \caption{NASBench201 Simulation with 8x Acceleration}
+    \label{fig:nasbench_8x_acceleration}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+        \input{../evolution/nasbench_16_rank_error_correlations.pgf}
+    \end{center}
+    \caption{NASBench201 Rank Error Correlations with Rank}
+    \label{fig:nasbench_rank_error_correlations}
+\end{figure}
+
+\FloatBarrier
+\clearpage
+\subsection{NASNet Population Details}
+
+Using these possible ops
+
+Each evaluated to 16 epochs, how big is population?
+
+hyperparameters are as follows.
+
+UPDATE CHARTS TO INDICATE WHAT ORANGE/BLUE MEANS
+
 \end{document}

### 2020-08-22 paper/gen.sh

@@ -1,0 +1,4 @@
+pushd ..
+python3 src/relative_predictions/RelativePredictions.py
+popd
+./build.sh

### 2020-08-22 src/model/MetaModel.py

@@ -689,6 +689,59 @@ class MetaModel(SerialData):
         return embedding
 
 
+def verify_mutations():
+    params = Hyperparameters()
+    params.parameters['TRAIN_ITERATIONS'] = 1
+    params.parameters['REDUCTION_EXPANSION_FACTOR'] = 2
+
+    dataset = ImageDataset.get_cifar10_reduced()
+
+    for i in range(50):
+        model = MetaModel(params)
+        model.populate_with_nasnet_metacells()
+        model.build_model(dataset.images_shape)
+
+        model.mutate()
+        model.mutate()
+        model.mutate()
+        model.clear_model()
+        tf.keras.backend.clear_session()
+
+
+def verify_load():
+    dir_path = os.path.join(evo_dir, 'test_load_v2')
+    if not os.path.exists(dir_path):
+        os.makedirs(dir_path)
+    params = Hyperparameters()
+    params.parameters['TRAIN_ITERATIONS'] = 1
+    params.parameters['REDUCTION_EXPANSION_FACTOR'] = 2
+
+    dataset = ImageDataset.get_cifar10_reduced()
+
+    for i in range(50):
+        model = MetaModel(params)
+        model.populate_with_nasnet_metacells()
+        model.build_model(dataset.images_shape)
+        model.save_model(dir_path)
+        model.save_metadata(dir_path)
+        model.clear_model()
+        tf.keras.backend.clear_session()
+
+        other_model = MetaModel.load(dir_path, model.model_name, True)
+
+        tf.keras.backend.clear_session()
+
+
+def update_hparams(dir_name):
+    dir_path = os.path.join(evo_dir, dir_name)
+    model_names = [x for x in os.listdir(dir_path) if os.path.isdir(os.path.join(dir_path, x))]
+
+    meta_models = [MetaModel.load(dir_path, x, False) for x in model_names]
+
+    for x in meta_models:
+        x.save_metadata(dir_path)
+
+
 if __name__ == '__main__':
     pass
 

### 2020-08-22 src/relative_predictions/RelativePredictions.py

@@ -4,6 +4,14 @@ import sys
 import scipy
 import scipy.stats
 import matplotlib.pyplot as plt
+import matplotlib
+matplotlib.use('pgf')
+matplotlib.rcParams.update({
+    "pgf.texsystem": "pdflatex",
+    'font.family': 'serif',
+    'text.usetex': True,
+    'pgf.rcfonts': False,
+})
 
 HERE = os.path.dirname(os.path.abspath(__file__))
 sys.path.append(os.path.join(HERE,'..\\'))
@@ -14,57 +22,49 @@ from model.MetaModel import  *
 from nas_201_api import NASBench201API as nasapi
 
 
-def verify_mutations():
-    params = Hyperparameters()
-    params.parameters['TRAIN_ITERATIONS'] = 1
-    params.parameters['REDUCTION_EXPANSION_FACTOR'] = 2
 
-    dataset = ImageDataset.get_cifar10_reduced()
-
+def random_exclusive(max_val, n):
+    all_vals = np.arange(max_val)
+    np.random.shuffle(all_vals)
+    return all_vals[:n]
 
 
-    for i in range(50):
-        model = MetaModel(params)
-        model.populate_with_nasnet_metacells()
-        model.build_model(dataset.images_shape)
-        # model.evaluate(dataset)
-
-        model.mutate()
-        model.mutate()
-        model.mutate()
-        model.clear_model()
-        tf.keras.backend.clear_session()
-        # model.mutate()
-        # model.mutate()
-        # model.mutate()
-        # model.mutate()
-        # model.mutate()
-        # model.mutate()
-        # model.mutate()
+def se(val1, val2):
+    return ((val1 - val2)**2)
 
 
-def verify_load():
-    dir_path = os.path.join(evo_dir, 'test_load_v2')
-    if not os.path.exists(dir_path):
-        os.makedirs(dir_path)
-    params = Hyperparameters()
-    params.parameters['TRAIN_ITERATIONS'] = 1
-    params.parameters['REDUCTION_EXPANSION_FACTOR'] = 2
+def ae(val1, val2):
+    return abs(val1 - val2)
 
-    dataset = ImageDataset.get_cifar10_reduced()
 
-    for i in range(50):
-        model = MetaModel(params)
-        model.populate_with_nasnet_metacells()
-        model.build_model(dataset.images_shape)
-        model.save_model(dir_path)
-        model.save_metadata(dir_path)
[…]

### 2020-08-22 src/relative_predictions/nas_bench_201_analysis.py

@@ -26,53 +26,7 @@ def load_nasbench201_accuraices():
     accs = np.swapaxes(accs, 0, 1)
     return accs
 
-def test():
 
-    size = 200
-    key = 888
-
-    api = get_api()
-
-    def qu(ind):
-        return api.query_by_index(ind, 'cifar10', f'{size}')[key]
-
-    def acc(entry, ind):
-        return (entry.get_eval('ori-test', ind)['accuracy'] / 100)
-
-    accs = [[] for _ in range(size)]
-
-    def app(i):
-        query = qu(i)
-        for e in range(size):
-            a = acc(query, e)
-            accs[e].append(a)
-
-    for i in range(len(api)):
-            app(i)
-
-    accs = np.array(accs)
-    print(accs.shape)
-    np.save(os.path.join(res_dir, f'nas_bench_201_cifar10_test_accuracies_{size}.npy'), accs)
-
-    # accs = np.swapaxes(accs, 0, 1)
-    #
-    # # scipy.stats.anderson(accs[-1])
-    # xvals = [x for x in range(len(api))]
-    #
-    # plt.subplot(1, 1, 1)
-    # plt.scatter(xvals, accs[-1])
-    # plt.show()
-
-    # num = len(api)
-    # print(f'api size: {num}')
-    # info = api.query_meta_info_by_index(1)
-    # print(f'info {info}')
-    # metrics = info.get_metrics('cifar10', 'test')
-    # print(f'metrics: {metrics}')
-    # test_acc = metrics['top1']
-    # print(f'test_acc: {test_acc}')
-    # # for i, arch_str in enumerate(api):
-    #     print('{:5d}/{:5d} : {:}'.format(i, len(api), arch_str))
 
 
 

### 2020-08-27 paper/paper.tex
paper updates

@@
 \usepackage{layout}
+\usepackage{booktabs}       % For \toprule, \midrule and \bottomrule
+\usepackage{siunitx}        % Formats the units and values
+\usepackage{pgfplotstable}  % Generates table from .csv
 
@@
 \setlength{\headsep}{5pt}
+
+\sisetup{
+    round-mode          = places, % Rounds numbers
+    round-precision     = 3, % to 3 places
+}
 
@@
 
-\subsection{Stochastic Search Experimentation}
+\section{Experiments}
 
-\subsubsection{Experiment Details}
+\subsection{Stochastic Search Experiments}
 To measure the potential of the use of z-scores and raw ranks as a predictors of final performance, populations of models are used to
@@
 
-Two populations of trained models from two different architecutre search spaces are sampled for this purpose.
-The first population is generated using a variety of hyperparemeter combinations within a search space similar to that of NASNet \cite{nasnet}.
-Implementation details of this search space are provided in the appendix. 
-The second population is a sampled subset of the architectures in NASBench201 \cite{nasbench201}.
+\subsubsection{Experiment Details}
+Three populations of trained models from two different architecutre search spaces are sampled.
+The first two populations are sampled subsets of the architectures available in NASBench201 \cite{nasbench201}.
+Each of these populations contains four subpopulations.
+The first population, \emph{NASBench201 100p}, has subpopulations consisting of 100 models each, the size of which is chosen to mirror the working population size 
+used in aging tournament selection experiments later in this paper.
+The second population, \emph{NASBench201 16p}, has subpopulations consisting of 16 models each, the size of which is chosen to mirror the number of models in the 
+subpopulations of the third population.
+The third population, \emph{NASNet 16p}, is generated four different hyperparemeter configurations within a search space similar to that of NASNet \cite{nasnet}.
+The subpopulations for each hyperparameter configuration consists of 16 models, each trained for 16 epochs.
+The purpose of this population is to be comparable in population size to the second population, but with significantly more network parameters.
+\textbf{WHAT ARE THESE NETWORK PARAMETER COUNTS?}
+Specific implementation details of this search space are provided in the appendix.
 
-Each population $P$ is evaluated at each combination between elements of $E^s$, $W^s$, and $M$.
+Each subpopulation $P$ undergoes a grid search, evaluating each combination between elements of $E^s$, $W^s$, and $M$.
 Each such evaluation at a given combination is referred to as a \emph{simulation}.
@@
 given a model, a prediction epoch, and a prediction window. 
-These metric functions include averaged-over-window z-score measurements \emph{zm}'s, and raw rank measurements \emph{rm}'s.
+These metric functions include averaged-over-window z-score measurements \emph{ZM}'s, and raw rank measurements \emph{RM}'s.
 
@@
 
-In each simulation, $P$ is shuffled then evaluated as an incremental subset of the shuffled population.
+In each simulation, $P$ is shuffled then evaluated incrementally.
 Thus, each simulation evaluates a simulated population as if it were growing to its final size, while using
@@
 Simlar to PNAS \cite{pnas}, the Spearman Coefficient is chosen to judge the reliability of early prediction of population performance ranks.
-At the addition of each subsequent model to the simulated population, average rank error, rank error for the newest model (new rank error), and the Spearman Coefficient
-for the population are measured and used as evaluation metrics. 
+At the addition of each subsequent model to the simulated population, proportaional average rank error (\emph{PARE}), proportional rank error for the newest model (\emph{PNRE}), and the Spearman Coefficient
+for the simulated population are measured and used as evaluation metrics. 
 Each simulation is run $N$ times, and evaluation metrics are averaged across simulation iterations. 
 Refer to the Figure ~\ref{fig:nasnet_1x_acceleration}, ~\ref{fig:nasnet_2x_acceleration}, ~\ref{fig:nasnet_4x_acceleration}, and ~\ref{fig:nasnet_8x_acceleration} in Appendix for simulation results.
-Additionally, the correlation between new models' predicted rank error and new models' predicted rank is measured for each simulation,
-and results are averaged across simulation iterations. These results can be found in Figure ~\ref{fig:rank_error_correlations}.
+Additionally, the correlation between new model's predicted rank and the corresponding PNRE is measured for each simulation,
+and results are averaged across simulation iterations and subpopulations. 
+Correlation results over evaluation metric tracked tightly, and these results were also invariant over different prediction window scalars, so results were averaged over
+these dimensions as well, for rank/PNRE correlations mapping directly to prediction epoch scalars (Table ~\ref{table:rank_error_corr}).
 
@@
 
-\textbf{Higher acceleration rates result in higher average and new rank error, and lower Spearman coefficients.}
-New rank error and Spearman ccoefficients converge to levels that show clear trend that increases with acceleration rate.
+Unless stated otherwise, only NASBench201 100p will be analyzed, since its increased population size decreases potential variance in measured properties.
+
+\textbf{Higher acceleration rates result in higher new rank error, and lower Spearman coefficients.}
+New rank error and Spearman ccoefficients converge to levels that show clear trends that increase and decrease respectively with acceleration rate.
 This is unsurprising, as these measurements are based on model performance that are further away in terms of epochs to their
 otherwise final performance. 
-As acceleration rate increases, average rank error comes closer to stabilizing around $\frac{1}{3}$, the expected average error rate
-for a random population, but the rank predictions causing such a rank error are clearly not random since the Spearman coefficient is far from zero.
+Independent of acceleration rate, average rank error appears to converge to $\frac{1}{3}$.
+This value is signicant since it's the expected distance between two points randomly sampled from two uniformly distributed variables over $[0, 1]$.
+The predicted and actual rankings, when divided by the simulated population size, are two such uniformly distributed variables, 
+thus it would also be expected for rankings that are predicted randomly to have a PARE near $\frac{1}{3}$.
+However, the rank predictions causing such a PARE are clearly not random since the Spearman coefficient is far from zero.
 
@@
 average rank error begins to stabilize around a population of 12.
+\textbf{HYPOTHESIZE WHY THIS MIGHT BE, implications for evo}
+
+\textbf{Prediction based on zscores and prediction based on raw ranks produce virtually the same results.}
+In all prediction epoch scalar/prediction window scalar combinations, ZMs and RMs have insignifcant marginal differences,
+with no clear trends of one being more effective than the other.
+In fact, the two are definitionally the same for populations trained to a number of epochs $X$ when
+
+\[1 >= XE^{s}W^{s} = W^{a}\]
+
+\textbf{PNRE has an overall weak-to-moderate positive correlation with the predicted new rank.}
+This trend is better observed with NASBench201 simulations, due to the fact that its larger simulated population will produce an innately more accurate
+representation of such a trend. 
+Across all prediction epoch scalars providing acceleration, the correlation between PNRE and predicted new rank is $0.437$,
+indicating a weak-to-moderate positive correlation. 
+This can be interpreted optimistically to suggest that, in an evolution context, the degree of exploration will be bolstered
+outside of the exploration facilitated by the evolutionary algorithm alone. 
+Pessimistically, this can be interpreted to suggest that suboptimal candidates might be chosen during the selection step of
+evolutionary selection algorithms, resulting in slower time to find better candidates or the possibility for better candidates
+to be spuriously removed from the population.
 
 \textbf{Model size appears to impact performance prediction accuracy.} 
-The NASNet model population is comprised of models which all are larger than their NASBench201 counterparts.
+As mentioned before, NASNet 16p is comprised of models which all are larger than their NASBench201 16p counterparts.
 With NASNet simulations, Spearman coefficients remain consistenly higher and new rank error levels off at a lower value in comparison to NASBench201 simulations.
 Nonetheless, NASNet simulations show an average rank error trajectories similar to the trajectories that NASBench201 simulations play out.
-\textbf{Where do average rank error/new rank error/spearman coeff actually level out to? - take last quarter and average it?}
+\textbf{HYPOTHESIZE}
 
-\textbf{Prediction based on zscores and prediction based on raw ranks produce virtually the same results.}
-This is more evident with NASBench201 since it draws out to a higher population size. 
-\textbf{CORRELATION?}
-
-\textbf{New rank error has an overall weak-to-moderate positive correlation with the predicted new rank itself.}
-This trend is better observed with NASBench201 simulations, due to the fact that its larger simulated population will produce an innately more accurate
-representation of such a trend. 
-\textbf{HOW DOES THIS CORRELATE WITH INCREASING ACCELERATION RATE?}
-This trend can be interpreted optimistically to suggest that, in an evolution context, degrees of exploration will be bolstered
-outside of the exploration facilitated by the evolutionary algorithm alone. 
-Pessimistically, this trend can be interpreted to suggest that suboptimal candidates might be chosen during the selection step of
-evolutionary selection algorithms, resulting in slower time to find better candidates or the possibility for better candidates
-to be spuriously removed.
-
-\section{Aging Search Experimentation}
+\subsection{Aging Search Experimentats}
 
@@
 selection mechanisms taking effect, since selection mechanisms generally increase the frequency of higher-performance candidates. 
-With a higher concentration of highly-performaning candidates in a population, the given evaluation metrics might perform less reliably.
+With a higher concentration of highly-performing candidates in a population, the given evaluation metrics might perform less reliably.
+To determine the reliability of the evaluation metrics in the context of an evolving population, NASBench201 is used as a search space
+over which aging tournament selection \cite{amoebanet} is used to conduct a search with a fixed time budget.
 
-testtest
+\subsubsection{Experiment Details}
 
-\section{Headings: first level}
-\label{headings}
+This experiment will use the same population configuration and evolutionary algorithm used in Amoebanet \cite{amoebanet}, where the population consists of 100 candidates at all times.
+An initial population of 100 is established.
+Then, at each selection step, 25 candidates are randomly selected; the best of which produces a mutated offspring.
+After the addition of the new, mutated offspring, the oldest candidate in the population is removed to maintain a population of 100.
 
-All headings should be lower case (except for first word and proper nouns),
-flush left, and bold.
+Similar to the previous experiment, a grid search is conducted over $E^s$, $W^s$, and $M$.
+Each combination is simulated 64 times, \textbf{and the same measurements are taken at each step, in addition to the actual performance of what is predicted to be the
+best candidate within the population at each step.}
+Each simulation is given a time budget equal to $max(E^{s})ND_{\mu}$, where $N$ is the size of the NASBench201 search space, and $D$ represents the NASBench201 training durations.
+This is intended to allow the possiblity of only the fastest acceleration exploring the entire NASBench201 search space.
 
-First-level headings should be in 12-point type.
+Results for this experiment's grid search are displayed in Figures \textbf{???}. 
+Additionally, Figure \textbf{???} shows the actual performance of what is predicted to be the best candidate within the population for each grid search configuration
+in respect to elapsed time.
 
-\subsection{Headings: second level}
+\subsubsection{Analysis}
 
-Second-level headings should be in 10-point type.
+\textbf{average population sizes per configuration, running metric triad, actual best performances over time ** vs time}
 
-\subsubsection{Headings: third level}
+%\section{Headings: first level}
+%\label{headings}
+%
+%All headings should be lower case (except for first word and proper nouns),
+%flush left, and bold.
+%
+%First-level headings should be in 12-point type.
+%
+%\subsection{Headings: second level}
+%
+%Second-level headings should be in 10-point type.
+%
+%\subsubsection{Headings: third level}
+%
+%Third-level headings should be in 10-point type.
+%
+%\subsection{Footnotes}
+%
+%Footnotes should be used sparingly.  If you do require a footnote, indicate
+%footnotes with a number\footnote{Sample of the first footnote.} in the
+%text. Place the footnotes at the bottom of the page on which they appear.
+%Precede the footnote with a horizontal rule of 2~inches (12~picas).
+%
+%Note that footnotes are properly typeset \emph{after} punctuation
+%marks.\footnote{As in this example.}
+%
+%
+%\subsection{Tables}
+%\begin{table}
+%  \caption{Sample table title}
+%  \label{sample-table}
+%  \centering
+%  \begin{tabular}{lll}
+%    \toprule
+%    \multicolumn{2}{c}{Part}                   \\
+%    \cmidrule(r){1-2}
+%    Name     & Description     & Size ($\mu$m) \\
+%    \midrule
+%    Dendrite & Input terminal  & $\sim$100     \\
+%    Axon     & Output terminal & $\sim$10      \\
+%    Soma     & Cell body       & up to $10^6$  \\
+%    \bottomrule
+%  \end{tabular}
+%\end{table}
 
-Third-level headings should be in 10-point type.
-
-\subsection{Footnotes}
-
-Footnotes should be used sparingly.  If you do require a footnote, indicate
-footnotes with a number\footnote{Sample of the first footnote.} in the
-text. Place the footnotes at the bottom of the page on which they appear.
-Precede the footnote with a horizontal rule of 2~inches (12~picas).
-
-Note that footnotes are properly typeset \emph{after} punctuation
-marks.\footnote{As in this example.}
-
-\subsection{Figures}
-
-\begin{figure}
-  \centering
-  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
-  \caption{Sample figure caption.}
-\end{figure}
-
-All artwork must be neat, clean, and legible. Lines should be dark enough for
-purposes of reproduction. The figure number and caption always appear after the
-figure. Place one line space before the figure caption and one line space after
-the figure. The figure caption should be lower case (except for first word and
-proper nouns); figures are numbered consecutively.
-
-You may use color figures.  However, it is best for the figure captions and the
-paper body to be legible if the paper is printed in either black/white or in
-color.
-
-\subsection{Tables}
-
-\begin{table}
-  \caption{Sample table title}
-  \label{sample-table}
-  \centering
-  \begin{tabular}{lll}
-    \toprule
-    \multicolumn{2}{c}{Part}                   \\
-    \cmidrule(r){1-2}
-    Name     & Description     & Size ($\mu$m) \\
-    \midrule
-    Dendrite & Input terminal  & $\sim$100     \\
-    Axon     & Output terminal & $\sim$10      \\
-    Soma     & Cell body       & up to $10^6$  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
+\FloatBarrier
+\clearpage
 \bibliography{reference}
@@
 \section{Appendix}
+
 \subsection{Stochastic Search Results}
 \subsubsection{NASNet Simulations}
+
 \begin{figure}[!h]
     \begin{center}
-        \input{../evolution/nasnet_1.0x_acceleration.pgf}
+        \input{../res/figures/nasnet_1x_acceleration.pgf}
     \end{center}
@@
 \end{figure}
+
 \begin{figure}
     \begin{center}
-        \input{../evolution/nasnet_2.0x_acceleration.pgf}
+        \input{../res/figures/nasnet_2x_acceleration.pgf}
     \end{center}
@@
     \begin{center}
-        \input{../evolution/nasnet_4.0x_acceleration.pgf}
+        \input{../res/figures/nasnet_4x_acceleration.pgf}
     \end{center}
@@
     \begin{center}
-        \input{../evolution/nasnet_8.0x_acceleration.pgf}
+        \input{../res/figures/nasnet_8x_acceleration.pgf}
     \end{center}
@@
     \label{fig:nasnet_8x_acceleration}
-\end{figure}
-
-\begin{figure}
-    \begin{center}
-        \input{../evolution/nasnet_rank_error_correlations.pgf}
-    \end{center}
-    \caption{NASNet Rank Error Correlations with Rank}
-    \label{fig:nasnet_rank_error_correlations}
 \end{figure}
@@
     \begin{center}
-        \input{../evolution/nasbench_16_1.0x_acceleration.pgf}
+        \input{../res/figures/nasbench_16_1x_acceleration.pgf}
     \end{center}
@@
     \begin{center}
-        \input{../evolution/nasbench_16_2.0x_acceleration.pgf}
+        \input{../res/figures/nasbench_16_2x_acceleration.pgf}
     \end{center}
@@
     \begin{center}
-        \input{../evolution/nasbench_16_4.0x_acceleration.pgf}
+        \input{../res/figures/nasbench_16_4x_acceleration.pgf}
     \end{center}
@@
     \begin{center}
-        \input{../evolution/nasbench_16_8.0x_acceleration.pgf}
+        \input{../res/figures/nasbench_16_8x_acceleration.pgf}
     \end{center}
@@
 
-\begin{figure}
+\FloatBarrier
+\clearpage
+\subsubsection{Simulation Points of Convergence}
+
+\begin{table}[!h]
     \begin{center}
-        \input{../evolution/nasbench_16_rank_error_correlations.pgf}
+        \caption{NASNet Points of Convergence}
+        \label{table:nasnet_convergence}
+        \pgfplotstabletypeset[col sep=comma]
+        {../res/figures/nasnet_convergences.csv}
     \end{center}
-    \caption{NASBench201 Rank Error Correlations with Rank}
-    \label{fig:nasbench_rank_error_correlations}
-\end{figure}
+\end{table}
+
+\begin{table}[!h]
+    \begin{center}
+        \caption{NASBench201 16p Points of Convergence}
+        \label{table:nasnet_convergence}
+        \pgfplotstabletypeset[col sep=comma]
+        {../res/figures/nasbench_16_convergences.csv}
+    \end{center}
+\end{table}
+
+\begin{table}
+    \begin{center}
+        \caption{NASBench201 100p Points of Convergence}
+        \label{table:nasnet_convergence}
+        \pgfplotstabletypeset[col sep=comma]
+        {../res/figures/nasbench_100_convergences.csv}
+    \end{center}
+\end{table}
 
@@
 \clearpage
+\subsection{Rank Error vs Rank Correlations}
+
+\begin{table}[!h]
+    \begin{center}
+        \begin{tabular}{c | c | c | c | c}
+            \toprule
+            Population          & 1x    & 2x    &4x     & 8x    \\
+            \midrule
+            NASBench201 16p     & 0.194 & 0.275 & 0.342 & 0.350 \\
+            NASBench201 100p    & 0.237 & 0.423 & 0.430 & 0.459 \\
+            NASNet 16p          & 0.217 & 0.402 & 0.389 & 0.345 \\
+            \bottomrule
+        \end{tabular}
+        \caption{Rank Error Correlation with Rank, Averaged over Subpopulation, Prediction Window Scalar, and Evaluation Metric}
+        \label{table:rank_error_corr}
+    \end{center}
+\end{table}
+
+%\begin{figure}[!h]
+%    \begin{center}
+%        \input{../res/figures/nasbench_16_rank_error_correlations.pgf}
+%    \end{center}
+%    \caption{NASBench201 16p Rank Error Correlations with Rank}
+%    \label{fig:nasbench_rank_error_correlations}
+%\end{figure}
+%
+%\begin{figure}[!h]
+%    \begin{center}
+%        \input{../res/figures/nasbench_100_rank_error_correlations.pgf}
+%    \end{center}
+%    \caption{NASBench201 100p Rank Error Correlations with Rank}
+%    \label{fig:nasbench_rank_error_correlations}
+%\end{figure}
+
+%\begin{figure}
+%    \begin{center}
+%        \input{../res/figures/nasnet_rank_error_correlations.pgf}
+%    \end{center}
+%    \caption{NASNet Rank Error Correlations with Rank}
+%    \label{fig:nasnet_rank_error_correlations}
+%\end{figure}
+
+\FloatBarrier
 \subsection{NASNet Population Details}

### 2020-08-27 paper/gen.sh

@@ -1,4 +1,4 @@
 pushd ..
 python3 src/relative_predictions/RelativePredictions.py
 popd
-./build.sh
+#./build.sh

### 2020-08-27 src/FileManagement.py

@@ -1,15 +1,17 @@
 import os
 import json
+from pathlib import Path
 
-HERE = os.path.dirname(os.path.abspath(__file__))
+HERE = Path(os.path.dirname(os.path.abspath(__file__)))
 
-evo_dir = os.path.join(HERE, '..\\evolution\\')
-res_dir = os.path.join(HERE, '..\\res\\')
-tensorboard_dir = os.path.join(HERE, '..\\tensorboard\\')
-model_save_dir = os.path.join(HERE, '..\\models\\')
-task_dataset_dir = os.path.join(HERE, '..\\task_datasets\\')
+evo_dir = HERE / '../evolution/'
+res_dir = HERE / '../res/'
+tensorboard_dir = HERE / '../tensorboard/'
+model_save_dir = HERE / '../models/'
+task_dataset_dir = HERE / '../task_datasets/'
+fig_dir = res_dir / 'figures/'
 
-dirs = [evo_dir, res_dir, tensorboard_dir, model_save_dir, task_dataset_dir]
+dirs = [evo_dir, res_dir, tensorboard_dir, model_save_dir, task_dataset_dir, fig_dir]
 
 
 def write_json_to_file(obj: dict, dir_path: str, name: str) -> None:

### 2020-08-27 src/Utils.py

@@ -18,3 +18,9 @@ def list_contains_list(list_of_lists, list_to_check):
         if not mismatch:
             return True
     return False
+
+def get_multi_dim(dims):
+    if len(dims) == 1:
+        return [None for _ in range(dims[0])]
+    else:
+        return [get_multi_dim(dims[1:]) for _ in range(dims[0])]

### 2020-08-27 src/model/MetaModel.py

@@ -577,7 +577,7 @@ class MetaModel(SerialData):
         return embedding
 
     def populate_from_embedding(self, embedding):
-        print(f'Populating model from embedding')
+        # print(f'Populating model from embedding')
         num_cells = len(self.hyperparameters.parameters['CELL_STACKS'])
         num_groups_per_cell = self.hyperparameters.parameters['GROUPS_PER_CELL']
         num_ops_per_group = self.hyperparameters.parameters['OPS_PER_GROUP']

### 2020-08-27 src/relative_predictions/RelativePredictions.py

@@ -1,25 +1,36 @@
 import os
 import sys
+from pathlib import Path
 
 import scipy
 import scipy.stats
 import matplotlib.pyplot as plt
 import matplotlib
-matplotlib.use('pgf')
-matplotlib.rcParams.update({
-    "pgf.texsystem": "pdflatex",
-    'font.family': 'serif',
-    'text.usetex': True,
-    'pgf.rcfonts': False,
-})
+import string
+from pandas import DataFrame
 
-HERE = os.path.dirname(os.path.abspath(__file__))
-sys.path.append(os.path.join(HERE,'..\\'))
+def is_linux():
+    return sys.platform == 'linux'
+
+if is_linux():
+    matplotlib.use('pgf')
+    matplotlib.rcParams.update({
+        "pgf.texsystem": "pdflatex",
+        'font.family': 'serif',
+        'text.usetex': True,
+        'pgf.rcfonts': False,
+    })
+
+from cycler import cycler
+
+HERE = Path(os.path.dirname(os.path.abspath(__file__)))
+sys.path.append(str(HERE / '../'))
 
 from Utils import list_contains_list
 from model.MetaModel import  *
 
 from nas_201_api import NASBench201API as nasapi
+
 
 
 
@@ -122,138 +133,173 @@ def multi_model_test(dir_name = 'static_analysis_samples', num_models=32, hparam
         eval_model()
 
 
+def zm_rank(accuracies, window):
+    zscores = scipy.stats.zscore(accuracies, axis=0)
+    windowed_zscores = zscores[:, -window:]
+    mean_zscores = np.mean(windowed_zscores, axis=1)
+    result = int(np.argmax(mean_zscores))
+    return result, get_ranks(mean_zscores)
+
+def rm_rank(accuracies, window):
+    ranks = get_ranks(accuracies)
+    windowed_ranks = ranks[:, -window:]
+    mean_ranks = np.mean(windowed_ranks, axis=1)
+    result = int(np.argmax(mean_ranks))
+    return result, get_ranks(mean_ranks)
+
 def _analyze_multiple(accuracies, num_simulations = 32, prefix=''):
 
     num_experiments = len(accuracies)
     num_epochs = [len(x[0]) for x in accuracies]
     num_models = len(accuracies[0])
 
-    # window_size_scalars = [1, .5, 1/3, 1/4, 1/8, 1/16]
-    # zscores = [scipy.stats.zscore(x, axis=0) for x in accuracies]
[…]

### 2020-08-30 paper/paper.tex
WIP

@@
 \usepackage{booktabs}       % For \toprule, \midrule and \bottomrule
+\usepackage{graphicx}
+\usepackage{multicol}
+
+\usepackage{pgfplotstable}  % Generates table from .csv
 \usepackage{siunitx}        % Formats the units and values
-\usepackage{pgfplotstable}  % Generates table from .csv
+\sisetup{
+    round-mode=places,
+    round-precision=3,
+    scientific-notation=false,
+}
+\usepgfplotslibrary{external} 
+\tikzexternalize
 
@@
 \setlength{\headsep}{5pt}
-
-\sisetup{
-    round-mode          = places, % Rounds numbers
-    round-precision     = 3, % to 3 places
-}
 
@@
     is the reduction of search time. Some recent approaches attempt to reduce
-    search time by using surrogate performance metric that predict performance
-    based on learning curves and/or architecture embeddings. 
-    In this paper, the efficacy of purely statistical methodology for accelerating
-    the search time of evolutionary algorithm oriented NAS approaches is assessed. Analysis of results
-    suggests that statistical methods do not provide meaningful search time reductions
-    within commonly used NAS search spaces.
+    search time by using surrogate models that predict performance
+    based on learning curves or architecture topologies. 
+    In this paper, the efficacy of purely a statistical methodology for accelerating
+    the search time of an evolutionary-algorithm-oriented architecture search is assessed. 
+    This methodology uses two different windowed measures of relative architecture preformance
+    to predict final relative performance.
+    Results suggest that such methodology does not enable acceleration via early stopping, 
+    but does improve search time by using a more efficent performance metric than directly measuring model performance.
 \end{abstract}
@@
 In recent years, various approaches to neural architecture search (NAS) have been 
-successful in discovering neural architectures in a variety of computer vision
-tasks as well as in language modeling, and INSERT SOMETHING. While many discovered architectures
-have achieved state-of-the-art performance on popular computer benchmarks,
-the compute cost of NAS acts as a significant obstacle.
+successful in discovering high-performance neural architectures in a variety of spaces, primarily computer vision.
+While many discovered architectures have achieved state-of-the-art performance on popular benchmarks, the compute cost of NAS acts as a significant obstacle.
 
 Works within the field have taken many different approaches to reducing search time.
-Of the most significance to this work is the approach of using a performance surrogate,
-which allows the prediction of an architecture's performance prior to training completion.
-The effectiveness of different executions of approach manifest themselves in efficiency improvements 
-all the way from early stopping to \cite{arch_pred_1} architecture analysis without the necessity to train.
-\cite{snas} \cite{darts} 
-\cite{arch_pred_1}
-\cite{econas}
-\cite{amoebanet}
-\cite{acc_pred_1}
-\cite{pnas}
-\cite{lemonade}
-\cite{nasnet}
-\cite{learning_curve_1}
-\cite{synthetic_samples}
-\cite{snas}
-\cite{enas}
-\cite{cars}
-\cite{rl_nas}
-\cite{evolved_transformer}
-\cite{multitask_1}
-\cite{mnas}
-\cite{obj_detection_1}
-\cite{hardware_darts}
+One common approach is the use of a surrogate predictor model,
+which allows the prediction of an architecture's performance prior to training completion, or sometimes prior to training altogether.
+This, however, comes with the downside of the predictor model requiring training data from the search space prior to being able to 
+act in the search space, creating a chicken-or-the-egg problem.
+While there are solutions to getting around this dilemma, this work seeks to remove the need for the surrogate model entirely.
 
-\subsection{Background and Related Work}
+\subsection {Neural Architecture Search Background}
 
-For NAS approaches utilizing genetic evolutionary algorithms, the means with which the algorithm determines the most and least fit candidates 
-for mutation and optionally removal hinges upon the ability to determine comparative performance between candidates. The go-to metric for 
-determining the performance of candidates with single-objective models is validation or test accuracy or error. However, recent approaches 
-have forgone ratio variables to measure perforance in favor of ordinal variables \cite{pnas}, since relative performance is the only necessity 
-for common selection strategies like traditional tournament selection and its variations, such as aging selection \cite{amoebanet}. 
-In the case of PNAS \cite{pnas}, a surrogate model is used to predict model performance in a way that ranks models approximately as they would
-be ranked as they would be using actual performance.
+Neural architecture search, generally defined as the automation of the design of neural network architectures, has made leaps and bounds within recent years.
+The field was pioneered in \emph{Neural Architecture Search with Reinforcement Learning} \cite{rl_nas} as a single-objective search for an image classifier architecture 
+with an unbounded search space, which achieved SOTA on Cifar-10.
+Since then, the field progressed significantly, all the while diversifying the approaches and goals for neural architecture search.
 
-\subsection{Approach}
+NASNet \cite{nasnet} pushed the field forward in the direction of scalability, showing that a bounded search space that could be stacked in the form
+of cells produced architectures for Cifar-10 which also scaled to perform well on ImageNet.
 
-Using a surrogate model to predict model rank has the downside of training surrogate model to predict in a space that's growing in parallel with the
-surrogate. PNAS \cite{pnas} proposes a clever solution to this which allows the surrogate to train over more data during the beginning of search.
+Some works have innovated in the direction of the search mechanism, moving away from a reinforcement learning driver, toward evolution-based \cite{amoebanet}
+or differentiable architecture search \cite{darts}.
+
+Other works have investigated alternative search objectives, such as implementing platform-aware searches \cite{mnas} \cite{hardware_darts}, 
+or multi-objective searches \cite{lemonade} which explores the Pareto fronts including network performance and network size.
+
+While the majority of recent works have remained within the image classification space, some have broken out of image classification and computer vision
+altogether to find solutions to language modelling, like \emph{The Evolved Transformer} \cite{evolved_transformer}.
+
+\subsection{Related Work}
+
+A major goal within the nerual architecture search field has been the reduction of search time.
+The reduction of search time has been achieved through approaches like parameter sharing \cite{enas} \cite{cars},
+the use of smaller performance proxies \cite{econas}, or performance preditors.
+PNAS used a reinforcement-learning-based surrogate model which predicted \emph{relative} network performance based on cell topology to drastically
+accelerate search. 
+Similarly, \emph{Peephole} \cite{peephole} predicts network performance based on network topology with a LSTM agent.
+A notable shortcoming of these approaches is the fact that the surrogate model requires retraining between different cell topologies.
+
+Rather than relying on cell topology to predict performance prior to training, some works attempt to predict performance based on learning curves.
+This was initially done with the objective of hyperparameter optimization \cite{hparam_opt_1} with a weighted probabilistic learning curve model.
+This was built upon with the addition of Bayesian models \cite{bayesian_pred} and \emph{v}-SVRs \cite{vsvr_pred}.
+Common among these approaches that utilize the learning curve for performance prediction is that they are used to predict model performance directly,
+rather than predicting a metric that correlates with model performance.
+
+Direct prediction of network performance is not always necessary. 
+As discussed in PNAS \cite{pnas}, the important quality of a predictor is the ability to rank models in same order as they would be ranked if ordered
+according to their true performances.
+This allows for the selection of the best models irrespective of their actual performances.
+
+A shortcoming of many surrogate model approaches is the fact that the surrogate model must be trained prior to or during the architecture search.
+PNAS \cite{pnas} proposes a clever solution to this which allows the surrogate to train quickly at the beginning of the search, while scaling as the search progresses.
 Its proposed approach is only possible due to the fact that the PNAS search space has the capability to expand its search space in a way that
-allows the initial, smaller search spaces to be representative of the later, larger search spaces in a way that is meaningful to the surrogate.
-Such an approach doesn't provide benefits to search spaces that aren't expandable in a manner similar to that of PNAS, which means a surrogate would
-have to train on architectures representing a complete search space.
+allows the initial, smaller search space to be representative of the later, larger search space in a way that maintains the relvance of the surrogate.
 
-Surrogate models are not the only way to predict candidate ranking. Two ways to represent relative performances of a population of candidates are the following 'performance metrics':
+\section{Approach}
 
-- Raw Rank Measurements Based on Candidate Accuracy
+All surrogate models come with the downside of requiring some amount of data to be used for training prior to being able to effectively predict performance.
+In this section, a method with which intrinsic properties of a population can be utilized to predict relative performances, is discussed.
 
-Rank measurements are a clear way to represent accuracies as ordinal data. No additional explanation is necessary.
+Two ways to represent relative performances of a population of candidates are the following 'performance metrics':
+\begin{itemize}
+    \item \emph{Raw ranks}: Given candidates trained to the same epoch, 
+        candidates can be evaluated at epoch up to and including the final epoch to determine their relative rankings based on performances at that epoch.
+    \item \emph{Z-scores}: Similar to raw ranks, candidates can be evaluated at an epoch according to the z-scores of their performances at that epoch.
+        Z-scores have the added benefit over raw ranks of providing a better indication of outliers in clusters, as is intrinsic with interval data 
+        in comparison to ordinal data.
+        Some of the meaningfulness of z-scores is lost due to the fact that model performances do not appear to fall in a normal distribution for at least one of the 
+        search spaces used later in this work, NASBench 201 \cite{nasbench201}.
+        In this space, final performances of models trained to 200 epochs on Cifar10 result in an Anderson-Darling test statistic of 2717.199 without a 
+        Box-Cox transform, and 718.514 with, strongly indicating that model performances do not fall within a normal distribution.
+        Nonetheless, z-scores still provide more information about relative model performances than raw ranks.
 
-- Z-Scores of Candidate Accuracy
+\end{itemize}
 
-Zz-scores of candidate performance can somewhat act as interval data and thus can better represent outliers and clusters in comparison to raw ranks. 
-Z-Scores are typically used with normal distributions.
-Model accuracies in NASBench 201 \cite{nasbench201} provide a complete view of the distributions of accuracies in what could be considered to be 
-a search space representative of common NAS search spaces. 
-An Anderson-Darling test over model test accuracies for Cifar10 (200 epochs) in NASBench201 produces a test statistic of 2717.199 
-(718.514 after a Box-Cox transform) indicates at all significance levels that model accuracies do not fall into a normal distribution. 
-Nonetheless, z-scores still provide a way to judge relative model performance.
+To be explicit, the relevant benefit of ordinal and interval performance metrics is that a population's measurements evaluated at an early epoch are 
+directly comparable to its measurements at a later epoch. 
+This is the basis for the possibility of search time acceleration, since the early performances have the potential to be predictive of final performances.
 
-The relevant benefit of ordinal and interval performance metrics is that a population's measurements evaluated at an early epoch are 
-directly comparable to its measurements at a later epoch. This is the basis for the possibility of search time acceleration, since
-the early performances have the potential to be predictive of final performances.
+Search time is accelerated by early stopping at epochs specified by scaling the total number of epochs $T$ by different \emph{prediction epoch scalars} in $E^s$,
 
-% \printinunitsof{in}\prntlen{\textwidth}
+\[E^s = \{1, 0.5, 0.25, 0.125\}\]
+
+This produces the actual \emph{prediction epochs} at which final model performance rank will be predicted, $E^{a}$.
+A number of epochs up to the prediction epoch are used to predict final performance. 
+The number of epochs which are used are specified by a \emph{prediction window} which is determined by scaling the prediction epoch
+by a \emph{prediction window scalar} from $W^s$
+
+\[W^s = \{1, 0.5, 0.25, 0.001\}\]
+
+This determines actual prediction windows $W^a$.
+Within each window, performance metrics defined by $M$ can be used to calculate relative performances at each epoch within the window.
+
+\[M = \{f_{zm}, f_{rm}\}\]
+
+As discussed before, these performance metrics include z-score measurements \emph{ZM}'s, and raw rank measurements \emph{RM}'s.
+Performance metrics are averaged over the window to produce final performance predictions for the population $P$.
+
+\[f_{zm}(x, e, w) = \frac{1}{e-w}\sum_{i=e-w}^{e}\frac{x_i - \mu_i}{\sigma_i}\]
+\[f_{rm}(x, e, w) = \frac{1}{e-w}\sum_{i=e-w}^{e}r_{x_{i}}(P)\]
+\[predictions(P, e, w, f_{predictor}) = r(map(P, f_{predictor}))\]
+\begin{center}
+where
+\end{center}
+\[r(P) = rank\ of\ every\ element\ in\ P\]
+\[r_{x}(P) = rank\ of\ x\ within\ P\]
 
@@
 Three populations of trained models from two different architecutre search spaces are sampled.
-The first two populations are sampled subsets of the architectures available in NASBench201 \cite{nasbench201}.
+The first two populations are sampled subsets of the architecture space available in NASBench201 \cite{nasbench201}.
 Each of these populations contains four subpopulations.
 The first population, \emph{NASBench201 100p}, has subpopulations consisting of 100 models each, the size of which is chosen to mirror the working population size 
-used in aging tournament selection experiments later in this paper.
+used in aging tournament selection experiments later in this work.
 The second population, \emph{NASBench201 16p}, has subpopulations consisting of 16 models each, the size of which is chosen to mirror the number of models in the 
@@
 Each such evaluation at a given combination is referred to as a \emph{simulation}.
-The set of \emph{prediction epoch scalars} $E^s$ scales $t$, the total number of epochs per model in $P$,
-to produce the actual \emph{prediction epochs} at which final model performance rank will be predicted, $E^{a}$.
-This facilitates early performance prediction and thus the potential for search acceleration.
-The set of \emph{prediction window scalars} $W^s$ scales $E^a$ to produce the actual \emph{prediction windows} to be used 
-over trained epochs to be used during evaluation, $W^a$.
-The set of \emph{evaluation metric} functions $M$ includes functions for calculating an evaluation metric,
-given a model, a prediction epoch, and a prediction window. 
-These metric functions include averaged-over-window z-score measurements \emph{ZM}'s, and raw rank measurements \emph{RM}'s.
-
-\[E^s = \{1, 0.5, 0.25, 0.125\}\]
-\[W^s = \{1, 0.5, 0.25, 0.001\}\]
-\[M = \{f_{zm}, f_{rm}\}\]
-
-\[f_{zm}(x, e, w) = \frac{1}{e-w}\sum_{i=e-w}^{e}\frac{x_i - \mu_i}{\sigma_i}\]
-\[f_{rm}(x, e, w) = \frac{1}{e-w}\sum_{i=e-w}^{e}r_{x_{i}}(P)\]
-
-\[predictions(P, e, w, f_{predictor}) = r(map(P, f_{predictor}))\]
-
-\[r(P) = rank\ of\ every\ element\ in\ P\]
-\[r_{x}(P) = rank\ of\ x\ within\ P\]
-
-In each simulation, $P$ is shuffled then evaluated incrementally.
+In each simulation, $P$ is shuffled, then evaluated incrementally.
 Thus, each simulation evaluates a simulated population as if it were growing to its final size, while using
-the evaluation metrics to estimate simulated population rankings at each step.
+the prediction metrics to estimate simulated population rankings at each step.
 This allows a direct comparison between the predicted rankings and actual rankings at each increment.
@@
 At the addition of each subsequent model to the simulated population, proportaional average rank error (\emph{PARE}), proportional rank error for the newest model (\emph{PNRE}), and the Spearman Coefficient
-for the simulated population are measured and used as evaluation metrics. 
+for the simulated population are measured and used as \emph{evaluation metrics}.
 Each simulation is run $N$ times, and evaluation metrics are averaged across simulation iterations. 
@@
 and results are averaged across simulation iterations and subpopulations. 
-Correlation results over evaluation metric tracked tightly, and these results were also invariant over different prediction window scalars, so results were averaged over
+Correlation results over prediction metric tracked tightly, and these results were also invariant over different prediction window scalars, so results were averaged over
 these dimensions as well, for rank/PNRE correlations mapping directly to prediction epoch scalars (Table ~\ref{table:rank_error_corr}).
@@
 
-\textbf{Higher acceleration rates result in higher new rank error, and lower Spearman coefficients.}
-New rank error and Spearman ccoefficients converge to levels that show clear trends that increase and decrease respectively with acceleration rate.
+\textbf{Earlier stopping result in higher new rank error, and lower Spearman coefficients.}
+New rank error and Spearman ccoefficients converge to levels that show clear trends that decrease and increase respectively with the prediction epoch scalar.
 This is unsurprising, as these measurements are based on model performance that are further away in terms of epochs to their
 otherwise final performance. 
-Independent of acceleration rate, average rank error appears to converge to $\frac{1}{3}$.
+Independent of early stopping, average rank error appears to converge to $\frac{1}{3}$.
 This value is signicant since it's the expected distance between two points randomly sampled from two uniformly distributed variables over $[0, 1]$.
@@
 representation of such a trend. 
-Across all prediction epoch scalars providing acceleration, the correlation between PNRE and predicted new rank is $0.437$,
+Across all prediction epoch scalars providing early stopping, the correlation between PNRE and predicted new rank is $0.437$,
 indicating a weak-to-moderate positive correlation. 
@@
 
-\subsection{Aging Search Experimentats}
+\subsection{Evolutionary Search Experiments}
 
@@
 Each simulation is given a time budget equal to $max(E^{s})ND_{\mu}$, where $N$ is the size of the NASBench201 search space, and $D$ represents the NASBench201 training durations.
-This is intended to allow the possiblity of only the fastest acceleration exploring the entire NASBench201 search space.
+This is intended to allow the possiblity of only the smallest prediction epoch scalar exploring the entire NASBench201 search space.
 
 Results for this experiment's grid search are displayed in Figures \textbf{???}. 
-Additionally, Figure \textbf{???} shows the actual performance of what is predicted to be the best candidate within the population for each grid search configuration
-in respect to elapsed time.
+Additionally, Figure ~\ref{fig:nasbench_best_perf_vs_size} shows the actual performance of the candidate predicted to be the best within the population for each grid search configuration,
+in respect to the number of models evalued so far.
 
@@
 
-\textbf{average population sizes per configuration, running metric triad, actual best performances over time ** vs time}
+\textbf{Searches with early stopping only result in better models at low time budgets.}
+As shown in Figure ~\ref{fig:nasbench_best_perf_vs_slice}, searches with early stopping only outperform normal searches early on within the allotted time budget.
+This provides an answer to the primary focus of this experiement: Using a statistical approach for early stopping and thus early stopping
+is shown to only provide advantages with low time budgets.
+In the case of this experiment, a low time budget signifies a buget equal to less than 10% of the expected time to fully explore the NASBench201 search space.
+
+\textbf{Normal search without early stopping performs better with windows that contain more than the last epoch.}
+With these simulations, normal search performs best with a window over all epochs, rather than only the last epoch which represents the true candidate performance.
+This suggests that candidates that perform better overall tend to be close to the candidates with the best performances within the search space.
+This is fairly impactful, since this implies that the traditional method of using final performace to be the judge of a model might not be the optimal
+metric for determining the best candidate during an evolutionary selection step.
+This comes with the stipulation that the time budget only allows partial exploration of the search space without early stopping.
+To determine the impact of a larger time budget on the performance of different windows with normal search, an ablation study will be conducted.
+
+\textbf{RM outperforms ZM in most cases.}
+In the vast majority of cases, RM results in lower PARE, PNRE, and Spearman Coefficients.
+This is represented in Table ~\ref{table:full_sim_nasnet_convergence}, where all measurement ratios with 5% or more advantage are to the advantage of RM.
+
+\subsection{Ablation Study: Impact of Windows without Early Stopping}
+
+This study will be composed of a narrowed version of the evolutionary experiment where normal search is evaluated with an expanded search time budget.
+Specifically, the search budget will be equal to the expected duration to fully explore NASBench 201 by brute-force. 
+It should be noted that the evolutionary algorithm encompases an identity mechanism which allows already-evaluated candidates to exist within the population.
+Thus, the algorithm does not provide the guarantee that the entire search space will be explored within the expected duration for full exploration.
+This caveat is reconciled by the fact that NASBench 201 contains a narrow search space in comparison to search spaces such as the NASNet variant used in this work
+which is $3.299\cdot10^{11}$ times larger. Results for this experiment can be found in \textbf{??????}
+
+\subsubsection{Analysis}
+
+Besides the very initial time steps in each search, searches with a window of 1 are shown to result in higher performances at faster rates in comparsion to all other
+window sizes. 
+Searches using only the last epoch's performance can be to be slowly converging toward the same performances, but expanding the search time budget further loses
+meaninfulness since the search space would at that point be better explored by brute force anyway.
+The impact of windows on normal search will thus need further evaluation on larger search spaces and larger time budgets in a future study.
+Regardless, these results suggest that search is at least initially accelerated by the use of a window over the entirity of trained epochs.
+
+\section{Discussion and Future Work}
+
+The primary contribution of this work is the demonstration that the use of a proxy metric for performance within evoluationary architecture search
+results in higher performances at fixed time budgets in comparison to direct performance measurement, within the NASBench 201 search space.
+If, in future work, this method is shown to carry over to different search spaces and macro-architectures, this provides a simple
+means to further improve search speed.
+Additionally, this work demonstrates that performance prediction at early stops using two different statistical measures does not provide meaningful search acceleration.
+
+As discussed in the ablation study, future directions include the verification of the primary contribution over larger search spaces and search time budgets.
+Additionally, the investigation into factors influencing the normality of population performance distrubtions across different search spaces
+could yield opportunities for approaches that rely on the normality of population distributions. 
+This is of course contingent on the absence of the possiblity for vanishing gradients among other similar problems, which otherwise would
+lead to inevitable clusters within the population.
 
@@
 \clearpage
-\onecolumn
 \appendix
@@
 
-\begin{figure}[!h]
+\begin{figure}
     \begin{center}
+        \resizebox{\columnwidth}{!}{
             \input{../res/figures/nasnet_1x_acceleration.pgf} 
-    \end{center}
+        }
         \caption{NASNet Simulation with 1x Acceleration}
         \label{fig:nasnet_1x_acceleration}
+    \end{center}
 \end{figure}
@@
     \begin{center}
+        \resizebox{\columnwidth}{!}{
             \input{../res/figures/nasnet_2x_acceleration.pgf} 
-    \end{center}
+        }
         \caption{NASNet Simulation with 2x Acceleration}
         \label{fig:nasnet_2x_acceleration}
+    \end{center}
 \end{figure}
@@
     \begin{center}
+        \resizebox{\columnwidth}{!}{
             \input{../res/figures/nasnet_4x_acceleration.pgf}
-    \end{center}
+        }
         \caption{NASNet Simulation with 4x Acceleration}
         \label{fig:nasnet_4x_acceleration}
+    \end{center}
 \end{figure}
@@
     \begin{center}
+        \resizebox{\columnwidth}{!}{
             \input{../res/figures/nasnet_8x_acceleration.pgf}
-    \end{center}
+        }
         \caption{NASNet Simulation with 8x Acceleration}
         \label{fig:nasnet_8x_acceleration}
+    \end{center}
 \end{figure}
+
+\FloatBarrier
+\onecolumn
 
@@
         \label{table:nasnet_convergence}
-        \pgfplotstabletypeset[col sep=comma]
-        {../res/figures/nasnet_convergences.csv}
+        \resizebox{\textwidth}{!}{
+            \pgfplotstabletypeset[
+                    col sep=comma,
+                    trim cells=true,
+                    every head row/.style={before row=\toprule,after row=\midrule},
+                    every last row/.style={after row=\bottomrule},
+                    every column/.style={numeric type,fixed,precision=3,dec sep align}
+                    ]{../res/figures/nasnet_convergences.csv}
+        }
     \end{center}
@@
         \label{table:nasnet_convergence}
-        \pgfplotstabletypeset[col sep=comma]
-        {../res/figures/nasbench_16_convergences.csv}
+        \resizebox{\textwidth}{!}{
+            \pgfplotstabletypeset[
+                col sep=comma,
+                trim cells=true,
+                every head row/.style={before row=\toprule,after row=\midrule},
+                every last row/.style={after row=\bottomrule},
+                every column/.style={numeric type,fixed,precision=3,dec sep align}
+                ]{../res/figures/nasbench_16_convergences.csv}
+        }
     \end{center}
@@
 
-\begin{table}
+\begin{table}[!h]
     \begin{center}
@@
         \label{table:nasnet_convergence}
-        \pgfplotstabletypeset[col sep=comma]
-        {../res/figures/nasbench_100_convergences.csv}
+        \resizebox{\textwidth}{!}{
+            \pgfplotstabletypeset[
+                col sep=comma,
+                trim cells=true,
+                every head row/.style={before row=\toprule,after row=\midrule},
+                every last row/.style={after row=\bottomrule},
+                every column/.style={numeric type,fixed,precision=3,dec sep align}
+                ]{../res/figures/nasbench_100_convergences.csv}
+        }
     \end{center}
@@
 \FloatBarrier
-\clearpage
-\subsection{Rank Error vs Rank Correlations}
+\subsubsection{Rank Error vs Rank Correlations}
 
@@
 
-%\begin{figure}[!h]
-%    \begin{center}
-%        \input{../res/figures/nasbench_16_rank_error_correlations.pgf}
-%    \end{center}
-%    \caption{NASBench201 16p Rank Error Correlations with Rank}
-%    \label{fig:nasbench_rank_error_correlations}
-%\end{figure}
-%
-%\begin{figure}[!h]
-%    \begin{center}
-%        \input{../res/figures/nasbench_100_rank_error_correlations.pgf}
-%    \end{center}
-%    \caption{NASBench201 100p Rank Error Correlations with Rank}
-%    \label{fig:nasbench_rank_error_correlations}
-%\end{figure}
+\FloatBarrier
+\subsection{Aging Tournament Search}
 
-%\begin{figure}
-%    \begin{center}
-%        \input{../res/figures/nasnet_rank_error_correlations.pgf}
-%    \end{center}
-%    \caption{NASNet Rank Error Correlations with Rank}
-%    \label{fig:nasnet_rank_error_correlations}
-%\end{figure}
+\begin{figure}[!h]
+    \begin{center}
+        \input{../res/figures/64_evosim_all_performances_over_size.pgf}
+    \end{center}
+    \caption{NASBench201 Simulation Performances vs History Size}
+    \label{fig:nasbench_best_perf_vs_size}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+        \input{../res/figures/64_evosim_all_performances_over_slices.pgf}
+    \end{center}
+    \caption{NASBench201 Simulation Performances vs Time Slice}
+    \label{fig:nasbench_best_perf_vs_slice}
+\end{figure}
+
+\begin{table}
+    \begin{center}
+        \caption{NASBench201 Points of Convergence}
+        \label{table:full_sim_nasnet_convergence}
+        \resizebox{\textwidth}{!}{
+            \pgfplotstabletypeset[
+                col sep=comma,
+                trim cells=true,
+                every head row/.style={before row=\toprule,after row=\midrule},
+                every last row/.style={after row=\bottomrule},
+                every column/.style={numeric type,fixed,precision=3,dec sep align}
+                ]{../res/figures/64_full_sim_convergences.csv}
+        }
+    \end{center}
+\end{table}
+
+\begin{figure}
+    \begin{center}
+        \input{../res/figures/64_evosim_1x_acceleration.pgf}
+    \end{center}
+    \caption{NASBench201 Simulation with No Acceleration}
+    \label{fig:evo_nasbench_1x_acceleration}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+        \input{../res/figures/64_evosim_2x_acceleration.pgf}
+    \end{center}
+    \caption{NASBench201 Simulation with 2x Acceleration}
+    \label{fig:evo_nasbench_2x_acceleration}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+        \input{../res/figures/64_evosim_4x_acceleration.pgf}
+    \end{center}
+    \caption{NASBench201 Simulation with 4x Acceleration}
+    \label{fig:evo_nasbench_4x_acceleration}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+        \input{../res/figures/64_evosim_8x_acceleration.pgf}
+    \end{center}
+    \caption{NASBench201 Simulation with 8x Acceleration}
+    \label{fig:evo_nasbench_8x_acceleration}
+\end{figure}
+
+\FloatBarrier
+\subsubsection{Aging Tournament Ablation Study}
+
+\begin{figure}
+    \begin{center}
+        \input{../res/figures/64_extended_evosim_1x_acceleration.pgf}
+    \end{center}
+    \caption{NASBench201 Simulation with No Acceleration}
+    \label{fig:evo_ext_nasbench_1x_acceleration}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+        \input{../res/figures/64_extended_evosim_all_performances_over_size.pgf}
+    \end{center}
+    \caption{NASBench201 Simulation with No Acceleration}
+    \label{fig:evo_ext_nasbench_all_perfs}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+        \input{../res/figures/64_extended_evosim_all_performances_over_slices.pgf}
+    \end{center}
+    \caption{NASBench201 Simulation with No Acceleration}
+    \label{fig:evo_ext_nasbench_best_at_slice}
+\end{figure}
 
@@
 
-Using these possible ops
+The search space is similar to that of NASNet, with only the modification of possible operations. 
+Possible operations include the following:
+\begin{multicols}{2}
+\begin{itemize}
+    \item Identity
+    \item Convolution 3x3
+    \item Depthwise Seperable Convolution 3x3
+    \item Depthwise Seperable Convolution 5x5
+    \item Depthwise Seperable Convolution 7x7
+    \item Average Pooling 3x3
+    \item Average Pooling 5x5
+    \item Max Pooling 3x3
+    \item Max Pooling 5x5
+    \item Depthwise Seperable Convolution 1x7 followed by Depthwise Seperable Convolution 7x1
+\end{itemize}
+\end{multicols}
 
-Each evaluated to 16 epochs, how big is population?
+This results in the search space of $(10^{5}\cdot(6! - 2!))^{2} = 5.155\cdot10^{15}$ architectures, in comparison to the NASNet space which
+has $(13^{5}\cdot(6! - 2!))^{2} = 7.107\cdot10^{16}$ architectures.
+The NASNet 16p population is comprised of the following six subpopulations specified by their hyperparameters, all of which are trained on Cifar-10.
+The population is intended to represent an architecture near the base architecture used to evaluate Cifar-10 in NASNet, in addition to a variety of smaller
+proxies.
 
-hyperparameters are as follows.
+\begin{table}[!h]
+    \begin{center}
+        \begin{tabular}{c | c | c | c | c | c}
+            \toprule
+            Subpopulation   & Layers & Normal Cells per Layer   & Filters   & Epochs   & Parameters ($\mu$)\\
+            \midrule
+            1               & 3      & 3                        & 24        & 16       & 1766642.5 \\
+            2               & 3      & 3                        & 24        & 32       & 1766642.5 \\
+            3               & 3      & 5                        & 24        & 16       & 2719517.5 \\
+            4               & 3      & 5                        & 32        & 16       & 4735204 \\
+            4               & 3      & 6                        & 32        & 16       & 5564662 \\
+            4               & 3      & 6                        & 32        & 32       & 5564662 \\
+            \bottomrule
+        \end{tabular}
+        \caption{NASNet Subpopulation Configurations}
+        \label{table:nasnet_details}
+    \end{center}
+\end{table}
 
-UPDATE CHARTS TO INDICATE WHAT ORANGE/BLUE MEANS
+\textbf{UPDATE CHARTS TO INDICATE WHAT ORANGE/BLUE MEANS}
 

### 2020-08-30 paper/build.sh

@@ -1,4 +1,4 @@
-pdflatex paper
+pdflatex --extra-mem-bot=10000000 -shell-escape paper
 bibtex paper
-pdflatex paper
-pdflatex paper
+pdflatex --extra-mem-bot=10000000 -shell-escape paper
+pdflatex --extra-mem-bot=10000000 -shell-escape paper

### 2020-08-30 paper/gen.sh

@@ -1,4 +1,4 @@
 pushd ..
-python3 src/relative_predictions/RelativePredictions.py
+python3 src/relative_predictions/RelativePredictions.py all
 popd
 #./build.sh

### 2020-08-30 src/model/MetaModel.py

@@ -536,6 +536,7 @@ class MetaModel(SerialData):
         graph.render(os.path.join(dir_path, self.model_name, 'graph.png'))
 
     def get_flops(self, dataset:ImageDataset):
+        '''THIS IS BROKEN RIGHT NOW, DO NOT USE'''
         if self.keras_model is None:
             return 0
 
@@ -543,26 +544,30 @@ class MetaModel(SerialData):
         session = tf.compat.v1.keras.backend.get_session()
 
         with session.as_default():
-            input_img = tf.ones((1,) + dataset.images_shape, dtype=tf.float32)
-            output_image = self.keras_model(input_img)
+            with self.keras_model._graph.as_default():
+                input_img = tf.ones((1,) + dataset.images_shape, dtype=tf.float32)
+                output_image = self.keras_model(input_img)
 
-            run_meta = tf.compat.v1.RunMetadata()
+                run_meta = tf.compat.v1.RunMetadata()
 
-            _ = session.run(output_image,
-                            options=tf.compat.v1.RunOptions(trace_level=tf.compat.v1.RunOptions.FULL_TRACE),
-                            run_metadata=run_meta,
-                            # feed_dict={input_img:np.reshape(dataset.test_images[0], (1,)+dataset.images_shape)}
-                            )
+                _ = session.run(output_image,
+                                options=tf.compat.v1.RunOptions(trace_level=tf.compat.v1.RunOptions.FULL_TRACE),
+                                run_metadata=run_meta,
+                                # feed_dict={input_img:np.reshape(dataset.test_images[0], (1,)+dataset.images_shape)}
+                                )
 
-            opts = tf.compat.v1.profiler.ProfileOptionBuilder.float_operation()
-            # opts['output'] = 'none'
-            flops = tf.compat.v1.profiler.profile(run_meta=run_meta, cmd='op', options=opts)
+                opts = tf.compat.v1.profiler.ProfileOptionBuilder.float_operation()
+                flops = tf.compat.v1.profiler.profile(run_meta=run_meta, cmd='op', options=opts)
 
-            return flops.total_float_ops
-
+                return flops.total_float_ops
+        #
+        # session = tf.compat.v1.keras.backend.get_session()
+        #
+        # # session = tf.compat.v1.Session()
+        #
         # run_meta = tf.compat.v1.RunMetadata()
         # opts = tf.compat.v1.profiler.ProfileOptionBuilder.float_operation()
[…]

### 2020-08-30 src/relative_predictions/RelativePredictions.py

@@ -32,7 +32,15 @@ from model.MetaModel import  *
 from nas_201_api import NASBench201API as nasapi
 
 
+def save_plt(s):
+    if is_linux():
+        plt.savefig(f'{s}.pgf')
+    else:
+        plt.savefig(f'{s}.jpg')
 
+def remove_lowercase(s):
+    table = str.maketrans('', '', string.ascii_lowercase)
+    return s.translate(table)
 
 def random_exclusive(max_val, n):
     all_vals = np.arange(max_val)
@@ -272,13 +280,6 @@ def _analyze_multiple(accuracies, num_simulations = 32, prefix=''):
     # print(f'metrics shape: {metrics.shape}') # dims = (prediction epochs, windows, population group, datapoint, steps, metric type)
     # print(f'rank corrs shape: {rank_corrs.shape}') # dims = (prediction epochs, windows, population group, metric type)
 
-    def save_plt(s):
-        # print(f'saving {s}')
-        if is_linux():
-            plt.savefig(f'{s}.pgf')
-        else:
-            plt.savefig(f'{s}.jpg')
-
     actual_width = 5.5
     height = actual_width
     point_names = ['Average Rank Error', 'New Rank Error', 'Spearman Coef']
@@ -310,7 +311,12 @@ def _analyze_multiple(accuracies, num_simulations = 32, prefix=''):
 
                 converge_cutoff = int(num_models/4)
                 converge = metrics[pred_ind, window_ind, :, datapoint, -converge_cutoff:, :].mean(axis=0).mean(axis=0)
+
                 datapoint_convergences.extend(converge)
+                if converge[1] == 0:
+                    datapoint_convergences.append(0)
+                else:
+                    datapoint_convergences.append(converge[0]/converge[1])
 
                 for population_ind in range(num_populations):
                     for metric_ind in range(num_eval_metrics):
@@ -327,18 +333,17 @@ def _analyze_multiple(accuracies, num_simulations = 32, prefix=''):
 
         plt.tight_layout()
         save_name = os.path.join(fig_dir, f'{fig_name}')
+        print(f'saving {save_name}')
         save_plt(save_name)
 
-    def remove_lowercase(s):
-        table = str.maketrans('', '', string.ascii_lowercase)
-        return s.translate(table)
 
     conv_frame = DataFrame(data=np.array(convergences))
-    col_names = ['Prediction Epoch', 'Window']
-    for datapoint_name in point_names:
[…]

### 2020-08-30 src/relative_predictions/nas_bench_201_analysis.py

@@ -1,35 +1,0 @@
-from nas_201_api import NASBench201API as nasapi
-import os
-import sys
-import numpy as np
-import scipy.stats
-import matplotlib.pyplot as plt
-
-HERE = os.path.dirname(os.path.abspath(__file__))
-sys.path.append(os.path.join(HERE,'..\\'))
-
-from FileManagement import *
-
-def get_api():
-    file_name = 'NAS-Bench-201-v1_1-096897.pth'
-    file_path = os.path.join(res_dir, file_name)
-
-    if os.path.exists(file_path):
-        api = nasapi(file_path)
-        return api
-    else:
-        return None
-
-
-def load_nasbench201_accuraices():
-    accs = np.load(os.path.join(res_dir, 'nas_bench_201_cifar10_test_accuracies.npy'))
-    accs = np.swapaxes(accs, 0, 1)
-    return accs
-
-
-
-
-
-
-if __name__ == '__main__':
-    test()

### 2020-08-31 paper/paper.tex
done tweaking stuff

@@
 
-\title{Placeholder Title}
+\title{Model-less Performance Prediction for Neural Architecture Search Acceleration}
 
@@
     One of the saught after objectives within neural architecture search
-    is the reduction of search time. Some recent approaches attempt to reduce
+    is the reduction of search time. Many recent approaches attempt to reduce
     search time by using surrogate models that predict performance
-    based on learning curves or architecture topologies. 
+    based on learning curves or model topologies. 
     In this paper, the efficacy of purely a statistical methodology for accelerating
@@
     Results suggest that such methodology does not enable acceleration via early stopping, 
-    but does improve search time by using a more efficent performance metric than directly measuring model performance.
+    but does improve search time by using a more efficent performance metric than the direct measure of model performance.
 \end{abstract}
@@
 
-NASNet \cite{nasnet} pushed the field forward in the direction of scalability, showing that a bounded search space that could be stacked in the form
-of cells produced architectures for Cifar-10 which also scaled to perform well on ImageNet.
+NASNet \cite{nasnet} pushed the field forward in the direction of scalability.
+NASNet used a bounded search space in the form of cells, which was combined with a fixed macro-architecture for different tasks.
+Cells that performed well on Cifar-10 within a smaller macro-architecture were shown to also perform well on ImageNet within a larger macro-architecture,
+showing the viability of a proxy task in combination with a cell-based architecture search.
 
-Some works have innovated in the direction of the search mechanism, moving away from a reinforcement learning driver, toward evolution-based \cite{amoebanet}
+Some works have innovated in the direction of the search mechanism, moving away from a reinforcement learning driver, toward evolution-based search\cite{amoebanet}
 or differentiable architecture search \cite{darts}.
@@
 Other works have investigated alternative search objectives, such as implementing platform-aware searches \cite{mnas} \cite{hardware_darts}, 
-or multi-objective searches \cite{lemonade} which explores the Pareto fronts including network performance and network size.
+or multi-objective searches \cite{lemonade} which explore Pareto fronts across network performance and network size.
 
-While the majority of recent works have remained within the image classification space, some have broken out of image classification and computer vision
-altogether to find solutions to language modelling, like \emph{The Evolved Transformer} \cite{evolved_transformer}.
+While the majority of recent works have remained within the image classification space, some have broken out of computer vision
+altogether to instead address spaces such as language modelling, like \emph{The Evolved Transformer} \cite{evolved_transformer}.
 
@@
 
-A major goal within the nerual architecture search field has been the reduction of search time.
-The reduction of search time has been achieved through approaches like parameter sharing \cite{enas} \cite{cars},
-the use of smaller performance proxies \cite{econas}, or performance preditors.
+The goals of the reduction of search time has been achieved through approaches like parameter sharing \cite{enas} \cite{cars},
+the use of smaller performance proxies \cite{econas}, or surrogate performance preditors.
 PNAS used a reinforcement-learning-based surrogate model which predicted \emph{relative} network performance based on cell topology to drastically
-accelerate search. 
+accelerate search times. 
 Similarly, \emph{Peephole} \cite{peephole} predicts network performance based on network topology with a LSTM agent.
-A notable shortcoming of these approaches is the fact that the surrogate model requires retraining between different cell topologies.
+A notable shortcoming of these approaches is the fact that the surrogate model requires retraining between fundamentally different cell topologies.
 
 Rather than relying on cell topology to predict performance prior to training, some works attempt to predict performance based on learning curves.
-This was initially done with the objective of hyperparameter optimization \cite{hparam_opt_1} with a weighted probabilistic learning curve model.
+This was initially done with the objective of hyperparameter optimization with a weighted probabilistic learning curve model\cite{hparam_opt_1}.
 This was built upon with the addition of Bayesian models \cite{bayesian_pred} and \emph{v}-SVRs \cite{vsvr_pred}.
-Common among these approaches that utilize the learning curve for performance prediction is that they are used to predict model performance directly,
+Common among these approaches that utilize the learning curve for performance prediction is the prediction of model performance directly,
 rather than predicting a metric that correlates with model performance.
@@
 
-All surrogate models come with the downside of requiring some amount of data to be used for training prior to being able to effectively predict performance.
+All surrogate models come with the downside of requiring some amount of training data prior to being able to effectively predict performance.
 In this section, a method with which intrinsic properties of a population can be utilized to predict relative performances, is discussed.
 
-Two ways to represent relative performances of a population of candidates are the following 'performance metrics':
+Two ways to represent relative performances of a population of candidates are the following \emph{performance metrics}:
 \begin{itemize}
     \item \emph{Raw ranks}: Given candidates trained to the same epoch, 
-        candidates can be evaluated at epoch up to and including the final epoch to determine their relative rankings based on performances at that epoch.
-    \item \emph{Z-scores}: Similar to raw ranks, candidates can be evaluated at an epoch according to the z-scores of their performances at that epoch.
+        candidates can be evaluated at epochs up to, and including, the final epoch to determine their relative rankings based on performances at that epoch.
+    \item \emph{Z-scores}: Similar to raw ranks, candidates can be evaluated at an epoch according to the z-scores of their performances at those epochs.
         Z-scores have the added benefit over raw ranks of providing a better indication of outliers in clusters, as is intrinsic with interval data 
         in comparison to ordinal data.
-        Some of the meaningfulness of z-scores is lost due to the fact that model performances do not appear to fall in a normal distribution for at least one of the 
-        search spaces used later in this work, NASBench 201 \cite{nasbench201}.
-        In this space, final performances of models trained to 200 epochs on Cifar10 result in an Anderson-Darling test statistic of 2717.199 without a 
+        Some of the meaningfulness of z-scores is lost due to the fact that model performances do not appear to fall in a normal distribution for the most prominent 
+        search space used later in this work, NASBench 201 \cite{nasbench201}.
+        In this space, the final performances of models trained to 200 epochs on Cifar10 result in an Anderson-Darling test statistic of 2717.199 without a 
         Box-Cox transform, and 718.514 with, strongly indicating that model performances do not fall within a normal distribution.
@@
 
-Search time is accelerated by early stopping at epochs specified by scaling the total number of epochs $T$ by different \emph{prediction epoch scalars} in $E^s$,
+Specifically, search time is accelerated by early stopping at epochs specified by scaling the total number of epochs that would otherwise be trained $T$ by 
+\emph{prediction epoch scalars} in $E^s$,
 
@@
 As discussed before, these performance metrics include z-score measurements \emph{ZM}'s, and raw rank measurements \emph{RM}'s.
-Performance metrics are averaged over the window to produce final performance predictions for the population $P$.
+Performance metrics are averaged over the window to produce final performance predictions for a population $P$.
 
@@
 \subsection{Stochastic Search Experiments}
-To measure the potential of the use of z-scores and raw ranks as a predictors of final performance, populations of models are used to
+To measure the effectiveness of the use of z-scores and raw ranks as a predictors of final performance, populations of models are used to
 emulate a stochastic search that is accelerated by early performance prediction. 
-While stochastic search is a far-from-optimal search algorithm, this experiment's goal is rather to provide insight into the reliability 
-using the two performance predictors to find the best candidates at different population sizes.
+While stochastic search is a far-from-optimal search algorithm, this is made irrelevant by the experiment's goal to simply provide insight into the reliability 
+of the two performance predictors in finding the best candidates at different population sizes.
 
@@
 Three populations of trained models from two different architecutre search spaces are sampled.
-The first two populations are sampled subsets of the architecture space available in NASBench201 \cite{nasbench201}.
-Each of these populations contains four subpopulations.
-The first population, \emph{NASBench201 100p}, has subpopulations consisting of 100 models each, the size of which is chosen to mirror the working population size 
+The first two populations are sampled subsets of the architecture space available in NASBench 201 \cite{nasbench201}.
+Each of these populations contains four subpopulations which are randomly sampled from the space.
+The first population, \emph{NASBench 201 100p}, has subpopulations consisting of 100 models each, the size of which is chosen to mirror the working population size 
 used in aging tournament selection experiments later in this work.
-The second population, \emph{NASBench201 16p}, has subpopulations consisting of 16 models each, the size of which is chosen to mirror the number of models in the 
+The second population, \emph{NASBench 201 16p}, has subpopulations consisting of 16 models each, the size of which is chosen to mirror the number of models in the 
 subpopulations of the third population.
-The third population, \emph{NASNet 16p}, is generated four different hyperparemeter configurations within a search space similar to that of NASNet \cite{nasnet}.
-The subpopulations for each hyperparameter configuration consists of 16 models, each trained for 16 epochs.
+The third population, \emph{NASNet 16p}, is generated by four different hyperparemeter configurations within a search space similar to that of NASNet \cite{nasnet}.
+The subpopulations for each hyperparameter configuration consists of 16 models each.
 The purpose of this population is to be comparable in population size to the second population, but with significantly more network parameters.
-\textbf{WHAT ARE THESE NETWORK PARAMETER COUNTS?}
+Specifically, the smallest average parameter count among all NASNet subpopulations is 1766642.5, while the estimated average for NASBench 201 is 99638.5, assuming
+the average parmeter count exposed through the NASBench 201 API, which is measured in MB, is representing float32 parameters.
 Specific implementation details of this search space are provided in the appendix.
@@
 This allows a direct comparison between the predicted rankings and actual rankings at each increment.
-Simlar to PNAS \cite{pnas}, the Spearman Coefficient is chosen to judge the reliability of early prediction of population performance ranks.
-At the addition of each subsequent model to the simulated population, proportaional average rank error (\emph{PARE}), proportional rank error for the newest model (\emph{PNRE}), and the Spearman Coefficient
+Simlar to PNAS \cite{pnas}, the Spearman coefficient is chosen to judge the reliability of early prediction of population performance ranks.
+At the addition of each subsequent model to the simulated population, proportaional average rank error (\emph{PARE}), proportional rank error for the newest model (\emph{PNRE}), and the Spearman coefficient
 for the simulated population are measured and used as \emph{evaluation metrics}.
 Each simulation is run $N$ times, and evaluation metrics are averaged across simulation iterations.
-Refer to the Figure ~\ref{fig:nasnet_1x_acceleration}, ~\ref{fig:nasnet_2x_acceleration}, ~\ref{fig:nasnet_4x_acceleration}, and ~\ref{fig:nasnet_8x_acceleration} in Appendix for simulation results.
-Additionally, the correlation between new model's predicted rank and the corresponding PNRE is measured for each simulation,
-and results are averaged across simulation iterations and subpopulations. 
-Correlation results over prediction metric tracked tightly, and these results were also invariant over different prediction window scalars, so results were averaged over
-these dimensions as well, for rank/PNRE correlations mapping directly to prediction epoch scalars (Table ~\ref{table:rank_error_corr}).
+
+Refer to Figures 
+~\ref{fig:nasnet_1x_acceleration}, 
+~\ref{fig:nasnet_2x_acceleration}, 
+~\ref{fig:nasnet_4x_acceleration},
+~\ref{fig:nasnet_8x_acceleration},
+~\ref{fig:nasbench_16_1x_acceleration},
+~\ref{fig:nasbench_16_2x_acceleration},
+~\ref{fig:nasbench_16_4x_acceleration},
+~\ref{fig:nasbench_16_8x_acceleration},
+~\ref{fig:nasbench_100_1x_acceleration},
+~\ref{fig:nasbench_100_2x_acceleration},
+~\ref{fig:nasbench_100_4x_acceleration},
+and ~\ref{fig:nasbench_100_8x_acceleration}
+in the Appendix for simulation results.
+Each configuration within the grid search is averaged over the last 25\% of the simulation to produce approximate points of convergence for each evaluation metric 
+(Table~\ref{table:nasnet_convergence},~\ref{table:nasbench_16_convergence},~\ref{table:nasbench_100_convergence}).
+Additionally, the correlation between new models' predicted rank and the corresponding PNRE is measured for each simulation,
+and results are averaged across simulation iterations, subpopulations, and prediction metrics to produce a direct mapping from prediction epoch scalar to correlation (Table~\ref{table:rank_error_corr}).
+
+\begin{table}[!h]
+    \begin{center}
+        \begin{tabular}{c | c | c | c | c}
+            \toprule
+            Population          & 1x    & 2x    &4x     & 8x    \\
+            \midrule
+            NASBench201 16p     & 0.194 & 0.275 & 0.342 & 0.350 \\
+            NASBench201 100p    & 0.237 & 0.423 & 0.430 & 0.459 \\
+            NASNet 16p          & 0.217 & 0.402 & 0.389 & 0.345 \\
+            \bottomrule
+        \end{tabular}
+        \caption{Stochastic Simulation: PNRE Correlation with Rank}
+        \label{table:rank_error_corr}
+    \end{center}
+\end{table}
 
@@
 average rank error begins to stabilize around a population of 12.
-\textbf{HYPOTHESIZE WHY THIS MIGHT BE, implications for evo}
+This suggests that new additions to the populations are more reliably ranked than existing candidates,
+but this is likely driven by outliers within the existing populations resulting in an inflated average.
 
 \textbf{Prediction based on zscores and prediction based on raw ranks produce virtually the same results.}
-In all prediction epoch scalar/prediction window scalar combinations, ZMs and RMs have insignifcant marginal differences,
-with no clear trends of one being more effective than the other.
-In fact, the two are definitionally the same for populations trained to a number of epochs $X$ when
+In Table~\ref{table:nasbench_100_convergence}, there are minimal cases where differences between ZM and RM values for PARE, PNRE, or Spearman coefficients are greater than 5\%,
+and these cases form no clear trend.
+In Tables~\ref{table:nasnet_convergence} and~\ref{table:nasbench_16_convergence}, there are more such cases, but there still does not appear to be a trend.
+In fact, ZM and RM are definitionally the same for populations trained to a number of epochs $X$ when
 
@@
 representation of such a trend. 
-Across all prediction epoch scalars providing early stopping, the correlation between PNRE and predicted new rank is $0.437$,
+Averaged across all prediction epoch scalars providing early stopping, the correlation between PNRE and predicted new rank is $0.378$,
 indicating a weak-to-moderate positive correlation. 
@@
 \textbf{Model size appears to impact performance prediction accuracy.} 
-As mentioned before, NASNet 16p is comprised of models which all are larger than their NASBench201 16p counterparts.
-With NASNet simulations, Spearman coefficients remain consistenly higher and new rank error levels off at a lower value in comparison to NASBench201 simulations.
-Nonetheless, NASNet simulations show an average rank error trajectories similar to the trajectories that NASBench201 simulations play out.
-\textbf{HYPOTHESIZE}
+As mentioned before, NASNet 16p is comprised of models which all are larger than their NASBench 201 16p counterparts.
+More importantly, the search space for the NASNet search space variant used in this work is $3.299\cdot10^{11}$ times larger than the NASBench 201 search space.
+With NASNet simulations, Spearman coefficients remain consistenly higher and PNRE levels off at a lower value in comparison to NASBench201 simulations.
+Nonetheless, NASNet simulations show PARE trajectories similar to the trajectories of NASBench 201 16p simulations.
+Overall, this suggests that performance prediction is more effective on larger search spaces in comparison to smaller ones.
 
@@
 With a higher concentration of highly-performing candidates in a population, the given evaluation metrics might perform less reliably.
-To determine the reliability of the evaluation metrics in the context of an evolving population, NASBench201 is used as a search space
+To determine the reliability of the evaluation metrics in the context of an evolving population, NASBench 201 is used as a search space
 over which aging tournament selection \cite{amoebanet} is used to conduct a search with a fixed time budget.
@@
 
-This experiment will use the same population configuration and evolutionary algorithm used in Amoebanet \cite{amoebanet}, where the population consists of 100 candidates at all times.
-An initial population of 100 is established.
+This experiment will use the same population configuration and evolutionary algorithm used in Amoebanet \cite{amoebanet}.
+To start the search, an initial population of 100 is established.
 Then, at each selection step, 25 candidates are randomly selected; the best of which produces a mutated offspring.
@@
 Similar to the previous experiment, a grid search is conducted over $E^s$, $W^s$, and $M$.
-Each combination is simulated 64 times, \textbf{and the same measurements are taken at each step, in addition to the actual performance of what is predicted to be the
-best candidate within the population at each step.}
-Each simulation is given a time budget equal to $max(E^{s})ND_{\mu}$, where $N$ is the size of the NASBench201 search space, and $D$ represents the NASBench201 training durations.
+Each combination is simulated 64 times, and the same measurements are taken at each step, in addition to recording the actual performance of what is predicted to be the
+best candidate within the population.
+Each simulation is given a time budget equal to $min(E^{s})ND_{\mu}$, where $N$ is the size of the NASBench 201 search space, and $D$ represents NASBench 201 training durations.
 This is intended to allow the possiblity of only the smallest prediction epoch scalar exploring the entire NASBench201 search space.
 
-Results for this experiment's grid search are displayed in Figures \textbf{???}. 
+Results for this experiment are displayed in Figures~\ref{fig:nasbench_best_perf_vs_size},~\ref{fig:nasbench_best_perf_vs_slice},
+~\ref{fig:evo_nasbench_1x_acceleration},
+~\ref{fig:evo_nasbench_2x_acceleration},
+~\ref{fig:evo_nasbench_4x_acceleration},
+and ~\ref{fig:evo_nasbench_8x_acceleration},
+as well as Table~\ref{table:full_sim_nasnet_convergence} which shows approximate evaluation metric convergences.
 Additionally, Figure ~\ref{fig:nasbench_best_perf_vs_size} shows the actual performance of the candidate predicted to be the best within the population for each grid search configuration,
 in respect to the number of models evalued so far.
+
+\begin{figure}[!ht]
+    \begin{center}
+        \resizebox{\columnwidth}{!}{
+            \input{../res/figures/64_evosim_all_performances_over_size.pgf}
+        }
+        \caption{NASBench 201 Evolution Simulation: Performances vs History Size.
+        Simulations with different prediction epoch scalars are identified by different stopping points.
+        A prediction epoch scalar of .125 generally outperforms .25, but a PES of 1 outperforms all others.}
+        \label{fig:nasbench_best_perf_vs_size}
+    \end{center}
+\end{figure}
+
+\begin{figure}[!ht]
+    \begin{center}
+        \resizebox{\columnwidth}{!}{
+            \input{../res/figures/64_evosim_all_performances_over_slices.pgf}
+        }
+        \caption{NASBench 201 Evolution Simulation: Time Utilized vs Best Configuration. 
+        PES 1 and WS 1 outperforms other configurations for approximately 75\% of the time budget, 
+        and configurations with PES 1 and any window scalar outperform other configurations for approximately 90\% of the time budget.}
+        \label{fig:nasbench_best_perf_vs_slice}
+    \end{center}
+\end{figure}
 
@@
 \textbf{Searches with early stopping only result in better models at low time budgets.}
-As shown in Figure ~\ref{fig:nasbench_best_perf_vs_slice}, searches with early stopping only outperform normal searches early on within the allotted time budget.
-This provides an answer to the primary focus of this experiement: Using a statistical approach for early stopping and thus early stopping
+As shown in Figure ~\ref{fig:nasbench_best_perf_vs_slice}, searches with early stopping only outperform searches without early stopping, coined \emph{normal searches},
+early on within the allotted time budget.
+
+This provides an answer to the primary focus of this experiement: Using a statistical approach for early stopping and thus search acceleartion
 is shown to only provide advantages with low time budgets.
-In the case of this experiment, a low time budget signifies a buget equal to less than 10% of the expected time to fully explore the NASBench201 search space.
+Specifically, this is case for this experiment when the budget is less than 2.5\% of the expected time to fully explore the NASBench 201 search space.
 
 \textbf{Normal search without early stopping performs better with windows that contain more than the last epoch.}
-With these simulations, normal search performs best with a window over all epochs, rather than only the last epoch which represents the true candidate performance.
+With these simulations, normal search performs best with a window over all epochs, rather than with only the last epoch which represents the true final candidate performance.
 This suggests that candidates that perform better overall tend to be close to the candidates with the best performances within the search space.
-This is fairly impactful, since this implies that the traditional method of using final performace to be the judge of a model might not be the optimal
+This is fairly impactful, since this implies that the traditional method of using final performace to rank a candidate might not be the optimal
 metric for determining the best candidate during an evolutionary selection step.
@@
 In the vast majority of cases, RM results in lower PARE, PNRE, and Spearman Coefficients.
-This is represented in Table ~\ref{table:full_sim_nasnet_convergence}, where all measurement ratios with 5% or more advantage are to the advantage of RM.
+This is represented in Table ~\ref{table:full_sim_nasnet_convergence}, where all measurement ratios with 5\% or more advantage are to the advantage of RM.
 
-\subsection{Ablation Study: Impact of Windows without Early Stopping}
+\subsection{Ablation Study: The Impact of Windows without Early Stopping}
 
-This study will be composed of a narrowed version of the evolutionary experiment where normal search is evaluated with an expanded search time budget.
-Specifically, the search budget will be equal to the expected duration to fully explore NASBench 201 by brute-force. 
-It should be noted that the evolutionary algorithm encompases an identity mechanism which allows already-evaluated candidates to exist within the population.
-Thus, the algorithm does not provide the guarantee that the entire search space will be explored within the expected duration for full exploration.
-This caveat is reconciled by the fact that NASBench 201 contains a narrow search space in comparison to search spaces such as the NASNet variant used in this work
-which is $3.299\cdot10^{11}$ times larger. Results for this experiment can be found in \textbf{??????}
+This study will be composed of a narrowed version of the evolutionary experiment where normal search is evaluated with a larger time budget.
+Specifically, the search budget will be equal to the expected duration to fully explore NASBench 201 via brute-force. 
+It should be noted that the evolutionary algorithm encompases an identity mechanism which allows already-evaluated candidates to exist within the population,
+therefore not guaranteeing that only new architectures are added to the population's history.
+As a result of this, the algorithm does not provide the guarantee that the entire search space will be explored within the expected duration for full exploration.
+This caveat is reconciled by the fact that NASBench 201 contains a narrow search space in comparison to search spaces such as the NASNet variant used in this work.
+Results for this experiment can be found in Figures~\ref{fig:evo_ext_nasbench_all_perfs},~\ref{fig:evo_ext_nasbench_best_at_slice}, and ~\ref{fig:evo_ext_nasbench_1x_acceleration}.
+
+\begin{figure}[!h]
+    \begin{center}
+        \resizebox{\columnwidth}{!}{
+            \input{../res/figures/64_extended_evosim_all_performances_over_size.pgf}
+        }
+        \caption{NASBench 201 Extended Evolution Simulation: Performances vs History Size}
+        \label{fig:evo_ext_nasbench_all_perfs}
+    \end{center}
+\end{figure}
 
@@
 
-Besides the very initial time steps in each search, searches with a window of 1 are shown to result in higher performances at faster rates in comparsion to all other
+Besides the very initial time steps in each search, searches with a window of 1 are shown to result in higher performances at earlier points in comparsion to all other
 window sizes. 
-Searches using only the last epoch's performance can be to be slowly converging toward the same performances, but expanding the search time budget further loses
-meaninfulness since the search space would at that point be better explored by brute force anyway.
-The impact of windows on normal search will thus need further evaluation on larger search spaces and larger time budgets in a future study.
-Regardless, these results suggest that search is at least initially accelerated by the use of a window over the entirity of trained epochs.
+Searches using only the last epoch's performance appear to be slowly converging toward the same performances, but further expansion of the search time budget loses
+meaninfulness since the search space would at that point be better explored via brute force anyway.
+The impact of windows on normal search will thus need further evaluation within larger search spaces and with larger time budgets in a future study.
+Regardless, these results suggest that search is at least initially accelerated by the use of a window over the entirety of trained epochs.
 
@@
 
-The primary contribution of this work is the demonstration that the use of a proxy metric for performance within evoluationary architecture search
+The primary contribution of this work is the demonstration that the use of a windowed proxy metric for performance within evoluationary architecture search,
 results in higher performances at fixed time budgets in comparison to direct performance measurement, within the NASBench 201 search space.
@@
 
-As discussed in the ablation study, future directions include the verification of the primary contribution over larger search spaces and search time budgets.
-Additionally, the investigation into factors influencing the normality of population performance distrubtions across different search spaces
+As discussed in the ablation study, future directions include the verification of the primary contribution within larger search spaces and with larger search time or compute budgets.
+Additionally, the investigation into factors influencing the normality of population performance distributions across different search spaces
 could yield opportunities for approaches that rely on the normality of population distributions. 
@@
 
-%\section{Headings: first level}
-%\label{headings}
-%
-%All headings should be lower case (except for first word and proper nouns),
-%flush left, and bold.
-%
-%First-level headings should be in 12-point type.
-%
-%\subsection{Headings: second level}
-%
-%Second-level headings should be in 10-point type.
-%
-%\subsubsection{Headings: third level}
-%
-%Third-level headings should be in 10-point type.
-%
-%\subsection{Footnotes}
-%
-%Footnotes should be used sparingly.  If you do require a footnote, indicate
-%footnotes with a number\footnote{Sample of the first footnote.} in the
-%text. Place the footnotes at the bottom of the page on which they appear.
-%Precede the footnote with a horizontal rule of 2~inches (12~picas).
-%
-%Note that footnotes are properly typeset \emph{after} punctuation
-%marks.\footnote{As in this example.}
-%
-%
-%\subsection{Tables}
-%\begin{table}
-%  \caption{Sample table title}
-%  \label{sample-table}
-%  \centering
-%  \begin{tabular}{lll}
-%    \toprule
-%    \multicolumn{2}{c}{Part}                   \\
-%    \cmidrule(r){1-2}
-%    Name     & Description     & Size ($\mu$m) \\
-%    \midrule
-%    Dendrite & Input terminal  & $\sim$100     \\
-%    Axon     & Output terminal & $\sim$10      \\
-%    Soma     & Cell body       & up to $10^6$  \\
-%    \bottomrule
-%  \end{tabular}
-%\end{table}
-
 \FloatBarrier
-\clearpage
 \bibliography{reference}
@@
 \FloatBarrier
-\clearpage
 \appendix
@@
 \subsection{Stochastic Search Results}
+\clearpage
 \subsubsection{NASNet Simulations}
 
-\begin{figure}
+\begin{figure}[!h]
     \begin{center}
-        \resizebox{\columnwidth}{!}{
+        \resizebox{0.9\columnwidth}{!}{
             \input{../res/figures/nasnet_1x_acceleration.pgf} 
         }
-        \caption{NASNet Simulation with 1x Acceleration}
+        \caption{NASNet 16p: 1 Prediction Epoch Scalar}
         \label{fig:nasnet_1x_acceleration}
@@
 
-\begin{figure}
+\begin{figure}[!h]
     \begin{center}
-        \resizebox{\columnwidth}{!}{
+        \resizebox{0.95\columnwidth}{!}{
             \input{../res/figures/nasnet_2x_acceleration.pgf} 
         }
-        \caption{NASNet Simulation with 2x Acceleration}
+        \caption{NASNet 16p: 0.5 Prediction Epoch Scalar}
         \label{fig:nasnet_2x_acceleration}
@@
 
-\begin{figure}
+\begin{figure}[!h]
     \begin{center}
-        \resizebox{\columnwidth}{!}{
+        \resizebox{0.95\columnwidth}{!}{
             \input{../res/figures/nasnet_4x_acceleration.pgf}
         }
-        \caption{NASNet Simulation with 4x Acceleration}
+        \caption{NASNet 16p: 0.25 Prediction Epoch Scalar}
         \label{fig:nasnet_4x_acceleration}
@@
 
-\begin{figure}
+\begin{figure}[!h]
     \begin{center}
-        \resizebox{\columnwidth}{!}{
+        \resizebox{0.95\columnwidth}{!}{
             \input{../res/figures/nasnet_8x_acceleration.pgf}
         }
-        \caption{NASNet Simulation with 8x Acceleration}
+        \caption{NASNet 16p: 0.125 Prediction Epoch Scalar}
         \label{fig:nasnet_8x_acceleration}
@@
 \end{figure}
-
-\FloatBarrier
-\onecolumn
 
@@
     \begin{center}
+        \resizebox{0.9\columnwidth}{!}{
             \input{../res/figures/nasbench_16_1x_acceleration.pgf}
+        }
+        \caption{NASBench 201 16p: 1 Prediction Epoch Scalar}
+        \label{fig:nasbench_16_1x_acceleration}
     \end{center}
-    \caption{NASBench201 Simulation with 1x Acceleration}
-    \label{fig:nasbench_1x_acceleration}
 \end{figure}
 
-\begin{figure}
+\begin{figure}[!h]
     \begin{center}
+        \resizebox{0.95\columnwidth}{!}{
             \input{../res/figures/nasbench_16_2x_acceleration.pgf}
+        }
+        \caption{NASBench 201 16p: 0.5 Prediction Epoch Scalar}
+        \label{fig:nasbench_16_2x_acceleration}
     \end{center}
-    \caption{NASBench201 Simulation with 2x Acceleration}
-    \label{fig:nasbench_2x_acceleration}
 \end{figure}
 
-\begin{figure}
+\begin{figure}[!h]
     \begin{center}
+        \resizebox{0.95\columnwidth}{!}{
             \input{../res/figures/nasbench_16_4x_acceleration.pgf}
+        }
+        \caption{NASBench 201 16p: 0.25 Prediction Epoch Scalar}
+        \label{fig:nasbench_16_4x_acceleration}
     \end{center}
-    \caption{NASBench201 Simulation with 4x Acceleration}
-    \label{fig:nasbench_4x_acceleration}
 \end{figure}
 
-\begin{figure}
+\begin{figure}[!h]
     \begin{center}
+        \resizebox{0.95\columnwidth}{!}{
             \input{../res/figures/nasbench_16_8x_acceleration.pgf}
+        }
+        \caption{NASBench 201 16p: 0.125 Prediction Epoch Scalar}
+        \label{fig:nasbench_16_8x_acceleration}
     \end{center}
-    \caption{NASBench201 Simulation with 8x Acceleration}
-    \label{fig:nasbench_8x_acceleration}
 \end{figure}
 
+\begin{figure}[!h]
+    \begin{center}
+        \resizebox{0.9\columnwidth}{!}{
+            \input{../res/figures/nasbench_100_1x_acceleration.pgf}
+        }
+        \caption{NASBench 201 100p: 1 Prediction Epoch Scalar}
+        \label{fig:nasbench_100_1x_acceleration}
+    \end{center}
+\end{figure}
+
+\begin{figure}[!h]
+    \begin{center}
+        \resizebox{0.95\columnwidth}{!}{
+            \input{../res/figures/nasbench_100_2x_acceleration.pgf}
+        }
+        \caption{NASBench 201 100p: 0.5 Prediction Epoch Scalar}
+        \label{fig:nasbench_100_2x_acceleration}
+    \end{center}
+\end{figure}
+
+\begin{figure}[!h]
+    \begin{center}
+        \resizebox{0.95\columnwidth}{!}{
+            \input{../res/figures/nasbench_100_4x_acceleration.pgf}
+        }
+        \caption{NASBench 201 100p: 0.25 Prediction Epoch Scalar}
+        \label{fig:nasbench_100_4x_acceleration}
+    \end{center}
+\end{figure}
+
+\begin{figure}[!h]
+    \begin{center}
+        \resizebox{0.95\columnwidth}{!}{
+            \input{../res/figures/nasbench_100_8x_acceleration.pgf}
+        }
+        \caption{NASBench 201 100p: 0.125 Prediction Epoch Scalar}
+        \label{fig:nasbench_100_8x_acceleration}
+    \end{center}
+\end{figure}
+
+\clearpage
 \FloatBarrier
-\clearpage
-\subsubsection{Simulation Points of Convergence}
+\onecolumn
+\subsubsection{Stochastic Simulation Points of Convergence}
 
@@
     \begin{center}
-        \caption{NASNet Points of Convergence}
-        \label{table:nasnet_convergence}
         \resizebox{\textwidth}{!}{
@@
         }
+        \caption{NASNet 16p: Points of Convergence}
+        \label{table:nasbench_16_convergence}
     \end{center}
 \end{table}
-
 \begin{table}[!h]
     \begin{center}
-        \caption{NASBench201 16p Points of Convergence}
-        \label{table:nasnet_convergence}
+
         \resizebox{\textwidth}{!}{
@@
         }
+        \caption{NASBench 201 16p: Points of Convergence}
+        \label{table:nasnet_convergence}
     \end{center}
 \end{table}
-
 \begin{table}[!h]
     \begin{center}
-        \caption{NASBench201 100p Points of Convergence}
-        \label{table:nasnet_convergence}
+
         \resizebox{\textwidth}{!}{
@@
         }
-    \end{center}
-\end{table}
-
-\FloatBarrier
-\subsubsection{Rank Error vs Rank Correlations}
-
-\begin{table}[!h]
-    \begin{center}
-        \begin{tabular}{c | c | c | c | c}
-            \toprule
-            Population          & 1x    & 2x    &4x     & 8x    \\
-            \midrule
-            NASBench201 16p     & 0.194 & 0.275 & 0.342 & 0.350 \\
-            NASBench201 100p    & 0.237 & 0.423 & 0.430 & 0.459 \\
-            NASNet 16p          & 0.217 & 0.402 & 0.389 & 0.345 \\
-            \bottomrule
-        \end{tabular}
-        \caption{Rank Error Correlation with Rank, Averaged over Subpopulation, Prediction Window Scalar, and Evaluation Metric}
-        \label{table:rank_error_corr}
+        \caption{NASBench 201 100p: Points of Convergence}
+        \label{table:nasbench_100_convergence}
     \end{center}
@@
 \subsection{Aging Tournament Search}
+\FloatBarrier
 
-\begin{figure}[!h]
+\begin{table}[!h]
     \begin{center}
-        \input{../res/figures/64_evosim_all_performances_over_size.pgf}
-    \end{center}
-    \caption{NASBench201 Simulation Performances vs History Size}
-    \label{fig:nasbench_best_perf_vs_size}
-\end{figure}
-
-\begin{figure}
-    \begin{center}
-        \input{../res/figures/64_evosim_all_performances_over_slices.pgf}
-    \end{center}
-    \caption{NASBench201 Simulation Performances vs Time Slice}
-    \label{fig:nasbench_best_perf_vs_slice}
-\end{figure}
-
-\begin{table}
-    \begin{center}
-        \caption{NASBench201 Points of Convergence}
-        \label{table:full_sim_nasnet_convergence}
         \resizebox{\textwidth}{!}{
@@
         }
+        \caption{NASBench 201: Points of Convergence}
+        \label{table:full_sim_nasnet_convergence}
     \end{center}
 \end{table}
+\twocolumn
+
+\FloatBarrier
+\clearpage
 
@@
     \begin{center}
+        \resizebox{\columnwidth}{!}{
             \input{../res/figures/64_evosim_1x_acceleration.pgf}
+        }
+        \caption{NASBench 201: 1 Prediction Epoch Scalar}
+        \label{fig:evo_nasbench_1x_acceleration}
     \end{center}
-    \caption{NASBench201 Simulation with No Acceleration}
-    \label{fig:evo_nasbench_1x_acceleration}
 \end{figure}
@@
     \begin{center}
+        \resizebox{\columnwidth}{!}{
             \input{../res/figures/64_evosim_2x_acceleration.pgf}
+        }
+        \caption{NASBench 201: 0.5 Prediction Epoch Scalar}
+        \label{fig:evo_nasbench_2x_acceleration}
     \end{center}
-    \caption{NASBench201 Simulation with 2x Acceleration}
-    \label{fig:evo_nasbench_2x_acceleration}
 \end{figure}
@@
     \begin{center}
+        \resizebox{\columnwidth}{!}{
             \input{../res/figures/64_evosim_4x_acceleration.pgf}
+        }
+        \caption{NASBench 201: 0.25 Prediction Epoch Scalar}
+        \label{fig:evo_nasbench_4x_acceleration}
     \end{center}
-    \caption{NASBench201 Simulation with 4x Acceleration}
-    \label{fig:evo_nasbench_4x_acceleration}
 \end{figure}
@@
     \begin{center}
+        \resizebox{\columnwidth}{!}{
             \input{../res/figures/64_evosim_8x_acceleration.pgf}
+        }
+        \caption{NASBench 201: 0.125 Prediction Epoch Scalar}
+        \label{fig:evo_nasbench_8x_acceleration}
     \end{center}
-    \caption{NASBench201 Simulation with 8x Acceleration}
-    \label{fig:evo_nasbench_8x_acceleration}
 \end{figure}
@@
 
-\begin{figure}
+\begin{figure}[!h]
     \begin{center}
-        \input{../res/figures/64_extended_evosim_1x_acceleration.pgf}
+        \resizebox{0.9\columnwidth}{!}{
+            \input{../res/figures/64_extended_evosim_all_performances_over_slices.pgf}
+        }
+        \caption{NASBench 201: Time Utilized vs Best Configuration}
+        \label{fig:evo_ext_nasbench_best_at_slice}
     \end{center}
-    \caption{NASBench201 Simulation with No Acceleration}
-    \label{fig:evo_ext_nasbench_1x_acceleration}
 \end{figure}
 
-\begin{figure}
+\begin{figure}[!h]
     \begin{center}
-        \input{../res/figures/64_extended_evosim_all_performances_over_size.pgf}
+        \resizebox{0.9\columnwidth}{!}{
+            \input{../res/figures/64_extended_evosim_1x_acceleration.pgf}
+        }
+        \caption{NASBench 201: 1 Prediction Epoch Scalar}
+        \label{fig:evo_ext_nasbench_1x_acceleration}
     \end{center}
-    \caption{NASBench201 Simulation with No Acceleration}
-    \label{fig:evo_ext_nasbench_all_perfs}
 \end{figure}
+\onecolumn
 
-\begin{figure}
-    \begin{center}
-        \input{../res/figures/64_extended_evosim_all_performances_over_slices.pgf}
-    \end{center}
-    \caption{NASBench201 Simulation with No Acceleration}
-    \label{fig:evo_ext_nasbench_best_at_slice}
-\end{figure}
-
-\FloatBarrier
 \subsection{NASNet Population Details}
@@
 The population is intended to represent an architecture near the base architecture used to evaluate Cifar-10 in NASNet, in addition to a variety of smaller
-proxies.
+proxies. Population sizes are limited to 16 models due to compute constraints.
 
@@
     \begin{center}
+        \resizebox{0.9\columnwidth}{!}{
         \begin{tabular}{c | c | c | c | c | c}
@@
         \end{tabular}
+        }
         \caption{NASNet Subpopulation Configurations}
@@
 
-\textbf{UPDATE CHARTS TO INDICATE WHAT ORANGE/BLUE MEANS}
-
 \end{document}

### 2020-08-31 src/relative_predictions/RelativePredictions.py

@@ -288,6 +288,8 @@ def _analyze_multiple(accuracies, num_simulations = 32, prefix=''):
     x_ticks = (0, num_models, int(num_models / 4))
     x_models = [x for x in range(num_models)]
     color_pairs = [['#1f77b4', '#ff7f0e'], ['#2ca02c', '#d62728'], ['#9467bd', '#8c564b'], ['#e377c2', '#7f7f7f']]
+    datapoint_y_labels = ['Error', 'Error', 'Spr Coef']
+    datapoint_x_label = 'Population Size'
 
     convergences = []
 
@@ -309,6 +311,19 @@ def _analyze_multiple(accuracies, num_simulations = 32, prefix=''):
                     ax.xaxis.set_label_position('top')
                     ax.set_xlabel(point_names[datapoint])
 
+                if datapoint == 0:
+                    label_name = f'{window} window\n'
+                    if window_ind == len(chosen_windows) - 1:
+                        label_name += 'Error'
+                    ax.set_ylabel(label_name)
+                if window_ind == 0:
+                    ax.xaxis.set_label_position('top')
+                    ax.set_xlabel(point_names[datapoint])
+                if window_ind == len(chosen_windows) - 1:
+                    if datapoint != 0:
+                        ax.set_ylabel(datapoint_y_labels[datapoint])
+                    ax.set_xlabel(datapoint_x_label)
+
                 converge_cutoff = int(num_models/4)
                 converge = metrics[pred_ind, window_ind, :, datapoint, -converge_cutoff:, :].mean(axis=0).mean(axis=0)
 
@@ -323,12 +338,16 @@ def _analyze_multiple(accuracies, num_simulations = 32, prefix=''):
                         to_plot = metrics[pred_ind,window_ind,population_ind,datapoint,:,metric_ind]
                         c = cycler(color = [color_pairs[0][metric_ind]])
                         ax.set_prop_cycle(c)
-
-                        ax.plot(x_models, to_plot)
+                        if population_ind == 0:
+                            ax.plot(x_models, to_plot,label=metric_names[metric_ind])
+                        else:
+                            ax.plot(x_models, to_plot)
                         plt.xticks(np.arange(x_ticks[0], x_ticks[1], x_ticks[2]))
                         plt.xlim((x_ticks[0], x_ticks[1]))
[…]

### 2020-08-31 src/auto_dataset/TaskEvo.py
cleaned up the codebase

@@ -1,399 +1,0 @@
-from __future__ import annotations
-import matplotlib.pyplot as plt
-import os
-import sys
-import math
-import tensorflow as tf
-
-
-
-
-HERE = os.path.dirname(os.path.abspath(__file__))
-sys.path.append(os.path.join(HERE,'..\\'))
-
-from model.MetaModel import *
-from Hyperparameters import Hyperparameters
-from Utils import *
-from auto_dataset.TaskGen import DatasetGenerator, ObjectModifier
-
-
-
-def build_cell_model(cell: CellDataHolder, input_shape, num_filters, learning_rate):
-    cell_input = tf.keras.Input(input_shape)
-    cell_output = tf.keras.layers.Conv2D(num_filters, 1, 1, 'same')(cell_input)
-    cell_output = cell.build([cell_output, cell_output])
-    cell_output = cell_output[0]
-    cell_output = tf.keras.layers.Lambda(lambda x: tf.reduce_mean(input_tensor=x, axis=[1, 2]))(cell_output)
-    cell_output = tf.keras.layers.Dropout(.5)(cell_output)
-    cell_output = tf.keras.layers.Dense(10)(cell_output)
-    model = tf.keras.Model(inputs=cell_input, outputs=cell_output)
-    optimizer = tf.keras.optimizers.Adam(learning_rate=learning_rate)
-    model.compile(optimizer=optimizer, loss=tf.keras.losses.SparseCategoricalCrossentropy(from_logits=True), metrics=['accuracy'])
-    return model
-
-# gets the average accuracy on each test set of the dataset, of each cell in a model
-def test_model(metamodel: MetaModel, dataset: DatasetGenerator, cell_samples: int):
-    scalar = 4 # want to pretend that the drop path has this times many epochs to complete
-    steps_per_epoch = math.ceil(len(dataset.train_labels) / metamodel.hyperparameters.parameters['BATCH_SIZE'])
-    total_steps = metamodel.hyperparameters.parameters['TRAIN_ITERATIONS'] * metamodel.hyperparameters.parameters['TRAIN_EPOCHS'] * steps_per_epoch * scalar
-
-    # gets the accuracies for num_cell_samples on each test set of the dataset
-    def evaluate_meta_cell(meta_cell: MetaCell, num_cell_samples: int):
[…]

### 2020-08-31 src/auto_dataset/TaskGen.py

@@ -1,405 +1,0 @@
-from __future__ import annotations
-from enum import Enum, IntEnum
-
-from PIL import Image, ImageDraw, ImageEnhance
-import numpy as np
-import math
-from typing import List, Tuple
-import os
-import cv2
-
-from Dataset import ImageDataset
-from FileManagement import *
-from Utils import *
-
-def place(orig_img, new_img, coord) -> None:
-    new_size = (new_img.size[0] + coord[0], new_img.size[1] + coord[1])
-    shifted_image = new_img.transform(new_size, Image.AFFINE, (1, 0, -coord[0], 0, 1, -coord[1]))
-    orig_img.alpha_composite(shifted_image)
-
-
-def find_coeffs(pa, pb):
-    matrix = []
-    for p1, p2 in zip(pa, pb):
-        matrix.append([p1[0], p1[1], 1, 0, 0, 0, -p2[0]*p1[0], -p2[0]*p1[1]])
-        matrix.append([0, 0, 0, p1[0], p1[1], 1, -p2[1]*p1[0], -p2[1]*p1[1]])
-
-    A = np.matrix(matrix, dtype=np.float)
-    # A = np.array(matrix, dtype=np.float)
-    B = np.array(pb).reshape(8)
-
-    res = np.dot(np.linalg.inv(A.T * A) * A.T, B)
-    return np.array(res).reshape(8)
-
-
-def get_random_color() -> Tuple:
-    return (get_random_int(360, 0), 100, 100) #hsv rather than rgb
-
-
-class ObjectModifier(IntEnum):
-    SizeModifier = 1,
-    PerspectiveModifier = 2,
-    RotationModifier = 3,
-    ColorModifier = 4
-
-
-def _name_from_modifier(mod: ObjectModifier) -> str:
-    if mod == ObjectModifier.SizeModifier:
-        return 'size'
-    if mod == ObjectModifier.RotationModifier:
-        return 'rotation'
-    if mod == ObjectModifier.ColorModifier:
-        return 'color'
-    else:
-        return 'perspective'
-
-
-class ObjectRep:
-    def __init__(self, num_verticies: int, color: Tuple = None):
-        self.verticies = np.random.random((num_verticies, 2))
-        self.verticies = list(self.verticies)
-        self.verticies = [list(x) for x in self.verticies]
-
-        self.color = color #REPRESENTED AS HSV RATHER THAN RGB
-        if self.color is None:
-            self.color = get_random_color()
-
[…]

### 2020-08-31 src/relative_predictions/RelativePredictions.py

@@ -51,14 +51,12 @@ def random_exclusive(max_val, n):
 def se(val1, val2):
     return ((val1 - val2)**2)
 
-
 def ae(val1, val2):
     return abs(val1 - val2)
 
 
 def get_ranks(measurements):
     return np.argsort(np.argsort(measurements, axis=0), axis=0)
-
 
 def spearman_coef_distinct(rankings_predicted, rankings_actual):
     n = len(rankings_predicted)
@@ -69,7 +67,6 @@ def spearman_coef_distinct(rankings_predicted, rankings_actual):
     bottom = n * (n**2 - 1)
 
     return 1. - (top/bottom)
-
 
 def spearman_coef(rankings_predicted, rankings_actual):
     n = len(rankings_predicted)
@@ -84,7 +81,6 @@ def spearman_coef(rankings_predicted, rankings_actual):
         return 1.
 
     return cov / (std_pred*std_act)
-
 
 def multi_model_test(dir_name = 'static_analysis_samples', num_models=32, hparams=None, emb_queue=None):
     hyperparameters = Hyperparameters() if hparams is None else hparams
@@ -155,7 +151,7 @@ def rm_rank(accuracies, window):
     result = int(np.argmax(mean_ranks))
     return result, get_ranks(mean_ranks)
 
-def _analyze_multiple(accuracies, num_simulations = 32, prefix=''):
+def _stochastic_simulation(accuracies, num_simulations = 32, prefix=''):
 
     num_experiments = len(accuracies)
     num_epochs = [len(x[0]) for x in accuracies]
@@ -276,9 +272,7 @@ def _analyze_multiple(accuracies, num_simulations = 32, prefix=''):
         metrics = np.load(sim_paths[0])
         rank_corrs = np.load(sim_paths[1])
     num_populations = metrics.shape[2]
-    # print('finished loading')
-    # print(f'metrics shape: {metrics.shape}') # dims = (prediction epochs, windows, population group, datapoint, steps, metric type)
-    # print(f'rank corrs shape: {rank_corrs.shape}') # dims = (prediction epochs, windows, population group, metric type)
+
 
     actual_width = 5.5
     height = actual_width
@@ -392,7 +386,7 @@ def _analyze_multiple(accuracies, num_simulations = 32, prefix=''):
 
     l = (' & ').join([str(np.round(x, 3)) for x in rank_corrs.mean(axis=3).mean(axis=2).mean(axis=1).tolist()])
[…]

### 2020-08-31 src/static_model_analysis/StaticAnalysis.py

@@ -1,522 +1,0 @@
-import os
-import sys
-
-import scipy
-import scipy.stats
-import matplotlib.pyplot as plt
-
-HERE = os.path.dirname(os.path.abspath(__file__))
-sys.path.append(os.path.join(HERE,'..\\'))
-
-from Utils import list_contains_list
-from model.MetaModel import  *
-
-
-
-
-def test_residual_ratio():
-    hyperparameters = Hyperparameters()
-
-
-    model = MetaModel(hyperparameters)
-    model.populate_from_embedding(MetaModel.get_nasnet_embedding())
-    model.cells[0].process_stuff()
-    model.cells[1].process_stuff()
-
-def multi_model_test(dir_name = 'static_analysis_samples', num_models=32, hparams=None, emb_queue=None):
-    hyperparameters = Hyperparameters() if hparams is None else hparams
-
-    dataset = ImageDataset.get_cifar10()
-
-    embeddings_queue = [] if emb_queue is None else emb_queue
-
-    dir_path = os.path.join(evo_dir, dir_name)
-    if not os.path.exists(dir_path):
-        os.makedirs(dir_path)
-
-    existing_model_names = [x for x in os.listdir(dir_path) if os.path.isdir(os.path.join(dir_path, x))]
-    metamodels = [MetaModel.load(dir_path, x, False) for x in existing_model_names]
-    existing_embeddings = [x.get_embedding() for x in metamodels]
-    remaining_embedding_queue = [x for x in embeddings_queue if not list_contains_list(existing_embeddings, x)]
-
-    unfinished_model_names = []
-    for metamodel in metamodels:
-        if len(metamodel.metrics.metrics['accuracy']) < metamodel.hyperparameters.parameters['TRAIN_ITERATIONS']:
-            unfinished_model_names.append(metamodel.model_name)
-
-    def eval_model(embedding = None, metamodel = None):
-        model = metamodel
-        if model is None:
-            model = MetaModel(hyperparameters)
-            if embedding is None:
-                model.populate_with_nasnet_metacells()
-            else:
-                model.populate_from_embedding(embedding)
-            model.build_model(dataset.images_shape)
-        model.evaluate(dataset, 1, dir_path)
-        model.save_metadata(dir_path)
-        model.save_model(dir_path)
-        model.generate_graph(dir_path)
-        model.clear_model()
[…]

### 2020-09-08 paper/paper.tex
final edits before first release

@@
 \usepackage{multicol}
+\usepackage{multirow}
+\usepackage[font=small,labelfont=bf]{caption}
 
@@
 \usepgfplotslibrary{external}
+
 \tikzexternalize
 
-\bibliographystyle{plainnat}
+\bibliographystyle{unsrtnat} %{plainnat}
 \setlength{\headsep}{5pt}
 
-\title{Model-less Performance Prediction for Neural Architecture Search Acceleration}
+\title{Model-less Performance Prediction for Neural Architecture Search Time Reduction}
+\date{First released September 8, 2020, Last edited \today}
 
@@
 \begin{abstract}
-    One of the saught after objectives within neural architecture search
+    One of the sought after objectives within neural architecture search
     is the reduction of search time. Many recent approaches attempt to reduce
@@
     based on learning curves or model topologies. 
-    In this paper, the efficacy of purely a statistical methodology for accelerating
+    In this paper, the efficacy of a statistical methodology for reducing
     the search time of an evolutionary-algorithm-oriented architecture search is assessed. 
@@
     to predict final relative performance.
-    Results suggest that such methodology does not enable acceleration via early stopping, 
-    but does improve search time by using a more efficent performance metric than the direct measure of model performance.
+    Results suggest that such methodology does not enable search time reduction via early stopping, 
+    but does improve search time by using a more efficent performance metric than a direct measure of model performance.
 \end{abstract}
@@
 In recent years, various approaches to neural architecture search (NAS) have been 
-successful in discovering high-performance neural architectures in a variety of spaces, primarily computer vision.
-While many discovered architectures have achieved state-of-the-art performance on popular benchmarks, the compute cost of NAS acts as a significant obstacle.
+successful in discovering high-performance neural network architectures in a variety of spaces, primarily computer vision.
+Many discovered architectures have achieved state-of-the-art performance on popular benchmarks such as Cifar10 and ImageNet \cite{nasnet}\cite{amoebanet}\cite{enas}\cite{darts}\cite{econas},
+but this is not without compute cost acting as a significant obstacle.
 
-Works within the field have taken many different approaches to reducing search time.
-One common approach is the use of a surrogate predictor model,
+Works within the field have taken on the reduction search time from multiple directions.
+One common approach is the use of a trained surrogate predictor model \cite{bayesian_pred}\cite{vsvr_pred}\cite{peephole}\cite{pnas},
 which allows the prediction of an architecture's performance prior to training completion, or sometimes prior to training altogether.
-This, however, comes with the downside of the predictor model requiring training data from the search space prior to being able to 
-act in the search space, creating a chicken-or-the-egg problem.
-While there are solutions to getting around this dilemma, this work seeks to remove the need for the surrogate model entirely.
+This, however, comes with the intrinsic downside of an initially untrained predictor model requiring training data from the search space prior to being able to 
+act in the search space, creating a circular dependency that guarantees initially inefficiency during the search process.
+There are solutions to getting around this dilemma \cite{pnas}, but early stopping facilitated by a model-less performance predictor
+avoids this problem entirely, since training the predictor is not required.
 
-\subsection {Neural Architecture Search Background}
+This work explores the utilization of a population of candidates' relative performances, 
+measured as direct rankings or z-scores then averaged across a window of trained epochs,
+as a means to predict candidate rankings before training completion. 
+Results indicate this method, in combination with early stopping, overall does not result in higher performing candidates being found sooner.
+However, the use of a window over the entirety of trained epochs is shown to result in 
+the discovery of better candidates in comparison to a baseline search that only utilizes the candidates' final performances, 
+and does so at a faster rate compared to the baseline.
 
-Neural architecture search, generally defined as the automation of the design of neural network architectures, has made leaps and bounds within recent years.
-The field was pioneered in \emph{Neural Architecture Search with Reinforcement Learning} \cite{rl_nas} as a single-objective search for an image classifier architecture 
-with an unbounded search space, which achieved SOTA on Cifar-10.
-Since then, the field progressed significantly, all the while diversifying the approaches and goals for neural architecture search.
+This method stands to improve search times and search results for approaches with candidates trained and incrementally evaluated across a number of epochs,
+meaning this work has a high level of potential applicability across the neural architecture search field.
 
-NASNet \cite{nasnet} pushed the field forward in the direction of scalability.
+\subsection {Neural Architecture Search}
+
+The field of neural architecture search was pioneered in \emph{Neural Architecture Search with Reinforcement Learning} \cite{rl_nas}, which
+positioned the field as, ``a new research direction for automatically finding good neural network architectures.''
+This work performed a single-objective search for an image classifier architecture with an unbounded search space, achieving SOTA on Cifar-10.
+Since then, the field has progressed significantly, all the while diversifying the approaches and goals for neural architecture search.
+
+NASNet \cite{nasnet} pushed the field forward in the direction of scalability and transferrability.
 NASNet used a bounded search space in the form of cells, which was combined with a fixed macro-architecture for different tasks.
 Cells that performed well on Cifar-10 within a smaller macro-architecture were shown to also perform well on ImageNet within a larger macro-architecture,
-showing the viability of a proxy task in combination with a cell-based architecture search.
+showing the viability of a proxy objective in combination with a cell-based architecture search.
 
@@
 While the majority of recent works have remained within the image classification space, some have broken out of computer vision
-altogether to instead address spaces such as language modelling, like \emph{The Evolved Transformer} \cite{evolved_transformer}.
+altogether to instead address spaces such as language modelling, as is the case with \emph{The Evolved Transformer} \cite{evolved_transformer}.
 
-\subsection{Related Work}
+\section{Related Work}
 
-The goals of the reduction of search time has been achieved through approaches like parameter sharing \cite{enas} \cite{cars},
-the use of smaller performance proxies \cite{econas}, or surrogate performance preditors.
-PNAS used a reinforcement-learning-based surrogate model which predicted \emph{relative} network performance based on cell topology to drastically
-accelerate search times. 
-Similarly, \emph{Peephole} \cite{peephole} predicts network performance based on network topology with a LSTM agent.
+The goal of the reduction of search time has been achieved through approaches such as parameter sharing \cite{enas} \cite{cars},
+the use of smaller performance proxies \cite{econas}, and surrogate performance preditors.
+
+PNAS\cite{pnas} used a reinforcement-learning-based surrogate model which predicted relative network performance based on cell topology to drastically
+reduce search times for a cell-based architecture search. 
+Similarly, \emph{Peephole} \cite{peephole} predicts network performance based on network topology using an LSTM agent.
 A notable shortcoming of these approaches is the fact that the surrogate model requires retraining between fundamentally different cell topologies.
 
-Rather than relying on cell topology to predict performance prior to training, some works attempt to predict performance based on learning curves.
+Rather than relying on cell topology to predict performance prior to training, some works attempt to predict performance based on learning curves\cite{bayesian_pred}\cite{vsvr_pred}.
 This was initially done with the objective of hyperparameter optimization with a weighted probabilistic learning curve model\cite{hparam_opt_1}.
@@
 Common among these approaches that utilize the learning curve for performance prediction is the prediction of model performance directly,
-rather than predicting a metric that correlates with model performance.
+rather than the prediction of a metric that correlates with model performance.
 
@@
 As discussed in PNAS \cite{pnas}, the important quality of a predictor is the ability to rank models in same order as they would be ranked if ordered
-according to their true performances.
+according to their actual performances.
 This allows for the selection of the best models irrespective of their actual performances.
 
-A shortcoming of many surrogate model approaches is the fact that the surrogate model must be trained prior to or during the architecture search.
-PNAS \cite{pnas} proposes a clever solution to this which allows the surrogate to train quickly at the beginning of the search, while scaling as the search progresses.
-Its proposed approach is only possible due to the fact that the PNAS search space has the capability to expand its search space in a way that
-allows the initial, smaller search space to be representative of the later, larger search space in a way that maintains the relvance of the surrogate.
+A shortcoming of some surrogate model approaches \cite{peephole}\cite{bayesian_pred}\cite{vsvr_pred} is the fact that the surrogate model must be trained prior to or during the architecture search.
+PNAS \cite{pnas} proposes a solution to this which allows the surrogate to train quickly at the beginning of the search, while scaling as the search progresses.
+More specifically, the PNAS search space has the capability to expand its search space such that the initial, smaller search space is representative of the later,
+larger search space in a way that maintains the relevance of the surrogate.
 
-\section{Approach}
+\section{Methodology}
 
-All surrogate models come with the downside of requiring some amount of training data prior to being able to effectively predict performance.
-In this section, a method with which intrinsic properties of a population can be utilized to predict relative performances, is discussed.
+All trained surrogate models come with the downside of requiring some amount of training data prior to being able to effectively predict performance.
+In this section, intrinsic properties of a population are utilized to predict relative performances.
 
@@
     \item \emph{Raw ranks}: Given candidates trained to the same epoch, 
-        candidates can be evaluated at epochs up to, and including, the final epoch to determine their relative rankings based on performances at that epoch.
+        candidates can be evaluated at epochs up to, and including, the final epoch to determine their relative rankings based on performances at those epochs.
     \item \emph{Z-scores}: Similar to raw ranks, candidates can be evaluated at an epoch according to the z-scores of their performances at those epochs.
-        Z-scores have the added benefit over raw ranks of providing a better indication of outliers in clusters, as is intrinsic with interval data 
+        Z-scores have the added benefit over raw ranks of providing a better indication of outliers in clusters, as is inherent with interval data 
         in comparison to ordinal data.
-        Some of the meaningfulness of z-scores is lost due to the fact that model performances do not appear to fall in a normal distribution for the most prominent 
+        Some of the meaningfulness of z-scores is lost due to the fact that model performances do not fall in a normal distribution for the most prominent 
         search space used later in this work, NASBench 201 \cite{nasbench201}.
@@
 directly comparable to its measurements at a later epoch. 
-This is the basis for the possibility of search time acceleration, since the early performances have the potential to be predictive of final performances.
+This is the basis for the possibility of search time reduction via early stopping, since the early performances have the potential to be predictive of final performances.
 
-Specifically, search time is accelerated by early stopping at epochs specified by scaling the total number of epochs that would otherwise be trained $T$ by 
+Specifically, search time is reduced by early stopping at epochs specified by scaling the total number of epochs that would otherwise be trained $T$ by 
 \emph{prediction epoch scalars} in $E^s$,
@@
 
-This produces the actual \emph{prediction epochs} at which final model performance rank will be predicted, $E^{a}$.
+Scaling $T$ by $E^s$ produces the actual \emph{prediction epochs} $E^{a}$ at which final model performance rank will be predicted.
 A number of epochs up to the prediction epoch are used to predict final performance. 
@@
 emulate a stochastic search that is accelerated by early performance prediction. 
-While stochastic search is a far-from-optimal search algorithm, this is made irrelevant by the experiment's goal to simply provide insight into the reliability 
-of the two performance predictors in finding the best candidates at different population sizes.
+Stochastic search provides the same expected outcome as other uninformed search strategies like a sequential, brute force search.
+This is contrary to three of the popular categories of search strategies in NAS, such as gradient descent strategies represented by DARTS\cite{darts}, 
+evolutionary algorithm strategies represented by PNAS\cite{pnas}, or reinforcement learning strategies represented by ENAS\cite{enas}, all of which are informed searches.
+That being said, the uninformed nature of stochastic search is made irrelevant by the experiment's goal to provide insight into the reliability 
+of the two performance predictors at finding the highest performing candidates at different population sizes.
 
@@
 subpopulations of the third population.
-The third population, \emph{NASNet 16p}, is generated by four different hyperparemeter configurations within a search space similar to that of NASNet \cite{nasnet}.
+The third population, \emph{NASNet 16p}, is generated by six different hyperparameter configurations within a search space similar to that of NASNet \cite{nasnet}.
+Though the population will be referred to in this work as NASNet 16p, this search space has different available operations compared to NASNet \cite{nasnet}, 
+with specifics and implementation details present in the appendix.
 The subpopulations for each hyperparameter configuration consists of 16 models each.
 The purpose of this population is to be comparable in population size to the second population, but with significantly more network parameters.
-Specifically, the smallest average parameter count among all NASNet subpopulations is 1766642.5, while the estimated average for NASBench 201 is 99638.5, assuming
-the average parmeter count exposed through the NASBench 201 API, which is measured in MB, is representing float32 parameters.
-Specific implementation details of this search space are provided in the appendix.
+Specifically, the smallest average parameter count among all NASNet 16p subpopulations is 1766642.5, while the estimated average for NASBench 201 is 99638.5, assuming
+the average parmeter count exposed through the NASBench 201 API, which is measured in MB, represents float32 parameters.
 
@@
 This allows a direct comparison between the predicted rankings and actual rankings at each increment.
-Simlar to PNAS \cite{pnas}, the Spearman coefficient is chosen to judge the reliability of early prediction of population performance ranks.
+Simlar to PNAS \cite{pnas}, a Spearman coefficient is chosen to judge the reliability of early prediction of population performance ranks.
 At the addition of each subsequent model to the simulated population, proportaional average rank error (\emph{PARE}), proportional rank error for the newest model (\emph{PNRE}), and the Spearman coefficient
@@
 
-Refer to Figures 
-~\ref{fig:nasnet_1x_acceleration}, 
-~\ref{fig:nasnet_2x_acceleration}, 
-~\ref{fig:nasnet_4x_acceleration},
-~\ref{fig:nasnet_8x_acceleration},
-~\ref{fig:nasbench_16_1x_acceleration},
-~\ref{fig:nasbench_16_2x_acceleration},
-~\ref{fig:nasbench_16_4x_acceleration},
-~\ref{fig:nasbench_16_8x_acceleration},
-~\ref{fig:nasbench_100_1x_acceleration},
-~\ref{fig:nasbench_100_2x_acceleration},
-~\ref{fig:nasbench_100_4x_acceleration},
-and ~\ref{fig:nasbench_100_8x_acceleration}
-in the Appendix for simulation results.
 Each configuration within the grid search is averaged over the last 25\% of the simulation to produce approximate points of convergence for each evaluation metric 
 (Table~\ref{table:nasnet_convergence},~\ref{table:nasbench_16_convergence},~\ref{table:nasbench_100_convergence}).
-Additionally, the correlation between new models' predicted rank and the corresponding PNRE is measured for each simulation,
-and results are averaged across simulation iterations, subpopulations, and prediction metrics to produce a direct mapping from prediction epoch scalar to correlation (Table~\ref{table:rank_error_corr}).
+Additionally, the correlation between new models' predicted ranks and the corresponding PNREs is measured for each simulation,
+and results are averaged across simulation iterations, subpopulations, prediction windows scalars, and prediction metrics to produce a direct mapping from prediction epoch scalar to correlation (Table~\ref{table:rank_error_corr}).
+Individual simulation results are availble in the Stochastic Search Results section in the appendix.
 
@@
             \toprule
-            Population          & 1x    & 2x    &4x     & 8x    \\
+            & \multicolumn{4}{c}{Prediction Epoch Scalar} \\
+            Population          & 1    & 0.5    & 0.25  & 0.125 \\
             \midrule
@@
 
-Unless stated otherwise, only NASBench201 100p will be analyzed, since its increased population size decreases potential variance in measured properties.
+Unless stated otherwise, NASBench201 100p will be assumed to be the subject of analysis, since its increased population size decreases potential variance in measured properties.
 
-\textbf{Earlier stopping result in higher new rank error, and lower Spearman coefficients.}
-New rank error and Spearman ccoefficients converge to levels that show clear trends that decrease and increase respectively with the prediction epoch scalar.
-This is unsurprising, as these measurements are based on model performance that are further away in terms of epochs to their
+\textbf{Earlier stopping results in higher new rank error, and lower Spearman coefficients.}
+New rank error and Spearman coefficients converge to levels that show clear trends which decrease and increase respectively with the prediction epoch scalar.
+This is unsurprising, as these measurements are based on model performances that are further away in terms of epochs to their
 otherwise final performance. 
@@
 In Table~\ref{table:nasbench_100_convergence}, there are minimal cases where differences between ZM and RM values for PARE, PNRE, or Spearman coefficients are greater than 5\%,
-and these cases form no clear trend.
+and cases where there is greater than a 5\% discrepancy form no clear trend.
 In Tables~\ref{table:nasnet_convergence} and~\ref{table:nasbench_16_convergence}, there are more such cases, but there still does not appear to be a trend.
@@
 \textbf{PNRE has an overall weak-to-moderate positive correlation with the predicted new rank.}
-This trend is better observed with NASBench201 simulations, due to the fact that its larger simulated population will produce an innately more accurate
-representation of such a trend. 
 Averaged across all prediction epoch scalars providing early stopping, the correlation between PNRE and predicted new rank is $0.378$,
@@
 More importantly, the search space for the NASNet search space variant used in this work is $3.299\cdot10^{11}$ times larger than the NASBench 201 search space.
-With NASNet simulations, Spearman coefficients remain consistenly higher and PNRE levels off at a lower value in comparison to NASBench201 simulations.
-Nonetheless, NASNet simulations show PARE trajectories similar to the trajectories of NASBench 201 16p simulations.
+With NASNet 16p simulations, Spearman coefficients remain consistenly higher and PNRE levels off at a lower value in comparison to NASBench 201 16p simulations.
+Nonetheless, NASNet 16p simulations show PARE trajectories similar to the trajectories of NASBench 201 16p simulations.
 Overall, this suggests that performance prediction is more effective on larger search spaces in comparison to smaller ones.
@@
 Similar to the previous experiment, a grid search is conducted over $E^s$, $W^s$, and $M$.
-Each combination is simulated 64 times, and the same measurements are taken at each step, in addition to recording the actual performance of what is predicted to be the
+Each combination is simulated 64 times, and evaluation metrics are recorded at each step, in addition to recording the actual performance of what is predicted to be the
 best candidate within the population.
 Each simulation is given a time budget equal to $min(E^{s})ND_{\mu}$, where $N$ is the size of the NASBench 201 search space, and $D$ represents NASBench 201 training durations.
-This is intended to allow the possiblity of only the smallest prediction epoch scalar exploring the entire NASBench201 search space.
+This is intended to allow the possiblity of only the smallest prediction epoch scalar exploring the entire NASBench201 search space within the time budget.
 
-Results for this experiment are displayed in Figures~\ref{fig:nasbench_best_perf_vs_size},~\ref{fig:nasbench_best_perf_vs_slice},
-~\ref{fig:evo_nasbench_1x_acceleration},
-~\ref{fig:evo_nasbench_2x_acceleration},
-~\ref{fig:evo_nasbench_4x_acceleration},
-and ~\ref{fig:evo_nasbench_8x_acceleration},
-as well as Table~\ref{table:full_sim_nasnet_convergence} which shows approximate evaluation metric convergences.
-Additionally, Figure ~\ref{fig:nasbench_best_perf_vs_size} shows the actual performance of the candidate predicted to be the best within the population for each grid search configuration,
-in respect to the number of models evalued so far.
+Individual experiment results are available in the Aging Tournament Search section in the appendix.
 
-\begin{figure}[!ht]
+\begin{figure}[!t]
     \begin{center}
@@
 As shown in Figure ~\ref{fig:nasbench_best_perf_vs_slice}, searches with early stopping only outperform searches without early stopping, coined \emph{normal searches},
-early on within the allotted time budget.
+early on within the allotted time budget. The degree of outperformance of all other searches by normal search is showcased in ~\ref{fig:nasbench_best_perf_vs_size}, 
+which shows the actual performance of the candidate predicted to be the best within the population for each grid search configuration,
+in respect to the number of models evalued so far.
 
-This provides an answer to the primary focus of this experiement: Using a statistical approach for early stopping and thus search acceleartion
+These results provide an answer to the part of the focus of this experiment: Using a statistical approach for early stopping and thus search time reduction
 is shown to only provide advantages with low time budgets.
@@
 \textbf{Normal search without early stopping performs better with windows that contain more than the last epoch.}
-With these simulations, normal search performs best with a window over all epochs, rather than with only the last epoch which represents the true final candidate performance.
+Within these simulations, normal search performs best with a window over all epochs, rather than over only the last epoch which represents the true final candidate performance.
 This suggests that candidates that perform better overall tend to be close to the candidates with the best performances within the search space.
-This is fairly impactful, since this implies that the traditional method of using final performace to rank a candidate might not be the optimal
+This is impactful, since this implies that the traditional method of using final performace to rank a candidate might not be the optimal
 metric for determining the best candidate during an evolutionary selection step.
 This comes with the stipulation that the time budget only allows partial exploration of the search space without early stopping.
-To determine the impact of a larger time budget on the performance of different windows with normal search, an ablation study will be conducted.
+To examine the impact of a larger time budget on the performance of different windows with normal search, an ablation study will be conducted.
 
 \textbf{RM outperforms ZM in most cases.}
-In the vast majority of cases, RM results in lower PARE, PNRE, and Spearman Coefficients.
+In the vast majority of cases, RM results in lower PARE and PNRE measurements, and higher Spearman Coefficients.
 This is represented in Table ~\ref{table:full_sim_nasnet_convergence}, where all measurement ratios with 5\% or more advantage are to the advantage of RM.
 
-\subsection{Ablation Study: The Impact of Windows without Early Stopping}
+\subsection{Ablation Study: The Impact of Windows on Normal Searches}
 
-This study will be composed of a narrowed version of the evolutionary experiment where normal search is evaluated with a larger time budget.
-Specifically, the search budget will be equal to the expected duration to fully explore NASBench 201 via brute-force. 
-It should be noted that the evolutionary algorithm encompases an identity mechanism which allows already-evaluated candidates to exist within the population,
+This study will be composed of a narrowed version of the previous evolutionary experiment, where normal search will evaluated with a larger time budget.
+Specifically, the search budget will be equal to the expected duration to fully explore the NASBench 201 search space with a brute-force search.
+It should be noted that the aging tournament selection algorithm encompases an identity mechanism which allows already-evaluated candidates to exist within the population,
 therefore not guaranteeing that only new architectures are added to the population's history.
 As a result of this, the algorithm does not provide the guarantee that the entire search space will be explored within the expected duration for full exploration.
-This caveat is reconciled by the fact that NASBench 201 contains a narrow search space in comparison to search spaces such as the NASNet variant used in this work.
-Results for this experiment can be found in Figures~\ref{fig:evo_ext_nasbench_all_perfs},~\ref{fig:evo_ext_nasbench_best_at_slice}, and ~\ref{fig:evo_ext_nasbench_1x_acceleration}.
+This caveat is reconciled by the fact that NASBench 201 contains a narrow search space in comparison to search spaces such as the NASNet variant used in this work,
+meaning applications of this method outside of NASBench 201 are far less likely to have the possibility of exploring the entire search space and consequently suffering from using
+a search method besides brute-force search.
+Individual results for this experiement can be found in the Aging Tournament Ablation Study subsection in the appendix.
 
@@
 Besides the very initial time steps in each search, searches with a window of 1 are shown to result in higher performances at earlier points in comparsion to all other
-window sizes. 
-Searches using only the last epoch's performance appear to be slowly converging toward the same performances, but further expansion of the search time budget loses
-meaninfulness since the search space would at that point be better explored via brute force anyway.
-The impact of windows on normal search will thus need further evaluation within larger search spaces and with larger time budgets in a future study.
-Regardless, these results suggest that search is at least initially accelerated by the use of a window over the entirety of trained epochs.
+window sizes (Figure~\ref{fig:evo_ext_nasbench_best_at_slice} in the appendix).
+Figure~\ref{fig:evo_ext_nasbench_all_perfs} shows that searches using only the last epoch's performance appear to be slowly converging toward the same performances, 
+but further expansion of the search time budget in additional experiments loses meaninfulness since the search space would at that point be better explored via brute force.
+The impact of windows on normal search will thus need further evaluation in larger search spaces and with larger time budgets in a future study.
+Regardless, these results suggest that search times are at least initially improved by the use of a window over the entirety of trained epochs.
 
-\section{Discussion and Future Work}
+\section{Conclusion}
 
-The primary contribution of this work is the demonstration that the use of a windowed proxy metric for performance within evoluationary architecture search,
-results in higher performances at fixed time budgets in comparison to direct performance measurement, within the NASBench 201 search space.
-If, in future work, this method is shown to carry over to different search spaces and macro-architectures, this provides a simple
-means to further improve search speed.
-Additionally, this work demonstrates that performance prediction at early stops using two different statistical measures does not provide meaningful search acceleration.
+In this work, two proxy performance metrics are measured over varying averaged windows, at varying early stopping points to predict relative final candidate performances within a population.
+This method is evaluated within the contexts of stochastic search and aging tournament search to determine the efficacy of the method when applied to neural architecture search.
+The primary contribution of this work is the demonstration that the use of a windowed proxy performance metric within evolutionary architecture search,
+results in higher performances at fixed time budgets in comparison to direct final performance measurement, within the NASBench 201 search space.
+If, in future work, this method is shown to carry over to different search spaces and macro-architectures, this provides a
+means to further improve search speeds and search results that is highly applicable to neural architecture search methods that do not already utilize a performance surrogate nor early stopping.
+Additionally, this work demonstrates that performance prediction with this method in conjunction with early stopping does not result in increased search efficiency.
 
-As discussed in the ablation study, future directions include the verification of the primary contribution within larger search spaces and with larger search time or compute budgets.
+\section{Future Work}
+
+As discussed in the ablation study, future directions include the verification of the primary contribution within larger search spaces and with larger search times or compute budgets.
 Additionally, the investigation into factors influencing the normality of population performance distributions across different search spaces
 could yield opportunities for approaches that rely on the normality of population distributions. 
-This is of course contingent on the absence of the possiblity for vanishing gradients among other similar problems, which otherwise would
+This is contingent on the absence of the possiblity for vanishing gradients among other similar problems, which otherwise would
 lead to inevitable clusters within the population.
@@
 \FloatBarrier
+
 \bibliography{reference}
@@
 
-\subsection{NASNet Population Details}
+\subsection{NASNet 16p Population Details}
 
-The search space is similar to that of NASNet, with only the modification of possible operations. 
-Possible operations include the following:
+The NASNet 16p search space is similar to that of NASNet\cite{nasnet}, with only the modification of possible operations. 
+Possible operations for this work's search space include the following:
 \begin{multicols}{2}
@@
 
-This results in the search space of $(10^{5}\cdot(6! - 2!))^{2} = 5.155\cdot10^{15}$ architectures, in comparison to the NASNet space which
+This results in the search space of $(10^{5}\cdot(6! - 2!))^{2} = 5.155\cdot10^{15}$ architectures, in comparison to the NASNet\cite{nasnet} space which
 has $(13^{5}\cdot(6! - 2!))^{2} = 7.107\cdot10^{16}$ architectures.
 The NASNet 16p population is comprised of the following six subpopulations specified by their hyperparameters, all of which are trained on Cifar-10.
-The population is intended to represent an architecture near the base architecture used to evaluate Cifar-10 in NASNet, in addition to a variety of smaller
+The population is intended to represent an architecture near the base architecture used to evaluate Cifar-10 in NASNet\cite{nasnet}, in addition to a variety of smaller
 proxies. Population sizes are limited to 16 models due to compute constraints.
@@
         }
-        \caption{NASNet Subpopulation Configurations}
+        \caption{NASNet 16p Subpopulation Configurations}
         \label{table:nasnet_details}

### 2020-09-08 src/scripts/ModelExperiments.py
codebase cleanup

@@ -1,492 +1,0 @@
-from __future__ import annotations
-import matplotlib.pyplot as plt
-import tensorflow as tf
-import os
-import sys
-import cv2
-import math
-
-HERE = os.path.dirname(os.path.abspath(__file__))
-sys.path.append(os.path.join(HERE, '..\\'))
-
-from model.MetaModel import *
-from auto_dataset.TaskGen import DatasetGenerator
-from Hyperparameters import Hyperparameters
-
-def test_accuracy_at_different_train_amounts():
-    dir_path = os.path.join(evo_dir, 'test_accuracy_epochs')
-    if not os.path.exists(dir_path):
-        os.makedirs(dir_path)
-    hyperparameters = Hyperparameters()
-    hyperparameters.parameters['POPULATION_SIZE'] = 32
-    hyperparameters.parameters['ROUNDS'] = 0
-    hyperparameters.parameters['TRAIN_EPOCHS'] = 1
-    hyperparameters.parameters['TRAIN_ITERATIONS'] = 16
-
-    dataset = ImageDataset.get_cifar10()
-
-    existing_sims = [x for x in os.listdir(dir_path) if 'small' not in x and '.png' not in x]
-
-    num_already_done = len(existing_sims)
-    num_remaining = hyperparameters.parameters['POPULATION_SIZE'] - num_already_done
-    total_todo = hyperparameters.parameters['POPULATION_SIZE']
-    population = []
-    for round_num in range(num_remaining):
-        print(f'Evaluating model {round_num + 1 + num_already_done} of {total_todo}')
-        new_candidate = MetaModel(hyperparameters)
-        new_candidate.populate_with_nasnet_metacells()
-        new_candidate.model_name = 'evo_' + str(time.time())  # this is redone here since all models are initialized within microseconds of eachother for init population
-        new_candidate.build_model(dataset.images_shape)
-        new_candidate.evaluate(dataset)
-        new_candidate.save_model(dir_path)
-        # new_candidate.metrics.metrics['accuracy'].extend([x + round_num for x in range(4)])
-        new_candidate.save_metadata(dir_path)
-        population.append(new_candidate)
-        new_candidate.clear_model()
-
-
-def convert_all_models():
-    dir_path = os.path.join(evo_dir, 'test_accuracy_epochs')
-    output_dir_path = os.path.join(evo_dir, 'test_accuracy_epochs_h5')
[…]

### 2020-09-08 src/scripts/sandbox.py

@@ -1,162 +1,0 @@
-import tensorflow as tf
-from Dataset import ImageDataset
-import os
-from FileManagement import *
-import time
-
-class SwapModel(tf.keras.Model):
-    def __init__(self):
-        super().__init__()
-
-        self.const_layer_1 = tf.keras.layers.Conv2D(64, 3, 1, 'same', activation='relu', name='const1')
-
-        self.swap_layer_2 = tf.keras.layers.Conv2D(64, 3, 1, 'same', activation='relu', name='swap2')
-
-        self.const_layer_3 = tf.keras.layers.Conv2D(64, 3, 1, 'same', activation='relu', name='const3')
-
-        self.flatten_layer_4 = tf.keras.layers.Flatten()
-
-        self.dense_5 = tf.keras.layers.Dense(64)
-
-        self.dense_6 = tf.keras.layers.Dense(10)
-
-
-    def call(self, inputs, training=False, mask=None):
-        layer = inputs
-        layer = self.const_layer_1(layer)
-        layer = self.swap_layer_2(layer)
-        layer = self.const_layer_3(layer)
-        layer = self.flatten_layer_4(layer)
-        layer = self.dense_5(layer)
-        layer = self.dense_6(layer)
-        return layer
-
-    def swap(self):
-        new_size = 128
-        self.swap_layer_2 = tf.keras.layers.SeparableConv2D(128, 3, 1, 'same', activation='relu', name='swapped2')
-        self.swap_layer_2.build([None, None, None, 64])
-        self.const_layer_3.build([None, None, None, 128])
-
-
-def test1():
-    dataset = ImageDataset.get_cifar10()
-
-    model = SwapModel()
-
-
-    optimizer = tf.keras.optimizers.Adam(0.001)
-    model.compile(optimizer=optimizer, loss=tf.keras.losses.SparseCategoricalCrossentropy(from_logits=True), metrics=['accuracy'])
-    model.fit(dataset.train_images, dataset.train_labels, epochs=1)
-
-    model.save('test_save')
-
-    model.evaluate(dataset.test_images, dataset.test_labels)
-
-    model.summary()
-    model.swap()
-    model.compile(optimizer=optimizer, loss=tf.keras.losses.SparseCategoricalCrossentropy(from_logits=True), metrics=['accuracy'])
-    model.summary()
-    print(model.layers)
-
-    model = tf.keras.models.load_model('test_save')
-    model.summary()
-
[…]
